 %----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass {resume} 
\setlength{\headheight}{0pt}
\usepackage[left=0.50in,top=0.55in,right=0.50in,bottom=0.55in]{geometry} % Document margins
\usepackage{color}
\usepackage [english]{babel}
\usepackage [autostyle, english = american]{csquotes}
\usepackage{hyperref}
\usepackage{xspace}
\usepackage{etaremune}
\newcommand{\R}{\textup{\textrm{R}}\xspace}
\newcommand{\meb}{{\bf Garrison, S. M.}\xspace}
\newcommand{\et}{\textit{et al}.\xspace}
\newcommand{\eg}{\textit{e.g},\xspace}
\newcommand{\student}{\hspace{-3.95pt}\textsuperscript{*}\hspace* {2 pt}}
\newlength{\wideitemsep}
\setlength{\wideitemsep}{\itemsep}
\addtolength{\wideitemsep}{-3pt}
\let\olditem\item
\renewcommand{\item}{\setlength{\itemsep}{\wideitemsep}\olditem}
\renewcommand*{\familydefault}{\sfdefault}
\name{\textrm{\LARGE{S}\small{(arah)} %\textsuperscript{``}
\LARGE{M}ason %\textsuperscript{''}
 Garrison}}
\address{Hobbs Building, Room 203 \\ Vanderbilt	University, Peabody College}
\nonfrenchspacing
%230 Appleton Place PMB #552 Nashville, TN 37203
\address{\href{www.smasongarrison.com}{www.smasongarrison.com} \\ sarah.m.garrison@vanderbilt.edu}
\begin{document}
\nonfrenchspacing
\thispagestyle{myheadings}
\markright{\em{\textrm \today}}
\hyphenation{influence}
\hyphenation{Vanderbilt}
\hyphenation{Simulation}
\hyphenation{PsychoPy}
\hyphenation{leadershipinstitute}
\hyphenation{LoveLogica}
\hyphenation{Regression}
\hyphenation{Exploratory}
\hyphenation{Modeling}
%----------------------------------------------------------------------------------------
%	EDUCATION4
%----------------------------------------------------------------------------------------

\begin{rSection}{\textrm{Education}}
{\bf Vanderbilt University, Peabody College } \hfill  {\em $\approx$ 2018} \\
Ph.D Program in Quantitative Methods %(and Individual Differences) 
\\
\hspace* {3 mm}\textit{Certificate: Experimental Education (in progress)}\\
\hspace* {3 mm}Advisor: Joseph L. Rodgers\medskip\\
\textbf{University of British Columbia}\hfill \textit{Fall 2015}\\ 
Quinn Exchange Fellow at the Department of Psychology\\
\hspace* {3 mm} Sponsor: Jeremy Biesanz\medskip\\
\textbf{University of Michigan, Ann Arbor}\hfill Summer 2014\\ 
Summer Scholar at the Interuniversity Consortium for Political and Social Research\medskip\\
{\bf Washington University in St. Louis, }\textit{magna cum laude} \hfill  {May 2013} \\ 
{\em A.B} in Economics \& Psychology\\
\hspace* {3 mm}Honors Thesis: Gender differences in a multilevel model of marital satisfaction after 20 years.  \\
\hspace* {3 mm}Thesis Advisor: Michael J. Strube%\medskip\\

\end{rSection}
%----------------------------------------------------------------------------------------
%	Interests
%----------------------------------------------------------------------------------------
\begin{rSection}{\textrm{Interests}} \begin{center}Differential Epidemiology $\bullet$ Genetically Informed Design $\bullet$ Intelligence $\bullet$ Kinship Modeling $\bullet$ Personality\end{center}
\end{rSection}
%----------------------------------------------------------------------------------------
%	Funds & Awards
%----------------------------------------------------------------------------------------
\begin{rSection}{\textrm{Awards \& Honors}}
UBC Quinn Exchange Fellowship (C\$3,000) \hfill{2015}\smallskip\\
Tennessee Psychological Association, 3\textsuperscript{rd} Place Undergraduate Poster Competition \hfill{2014}\smallskip\\
ICPSR Jerome M. Clubb Scholarship (\$4,000) \hfill{2014}\smallskip\\
Peabody Dean's Summer Scholarship (\$5,334)			    \hfill  {2013; 2014}\smallskip\\	
SMEP Workshop Travel Award (\$1,000) \hfill{2014}\smallskip\\
Vanderbilt Graduate Honor Fellowship (\$50,000)	\hfill  {2013 - 2018}\smallskip\\	
%Peabody \& Vanderbilt Travel Grants (\$10,000)      \hfill  {2013 - 2018}\smallskip\\
Peabody Dean's Fellowship (\$5,000)					\hfill  {2013}\smallskip\\
%Vanderbilt Technology Fund (\$1,000)				\hfill  {2013}\smallskip\\
Robert Hogan Family Foundation Travel Grant (\$1,200) 	\hfill  {2013}\smallskip\\
Hayek Fund for Future Scholars                      \hfill  {2013}\smallskip\\
WUStL Latin Honors \hfill  {2013}\smallskip\\
%WUStL Departmental Honors in Psychology \hfill  {2013}\smallskip\\
\textit{Sigma Xi} Science Honors Society                    			\hfill  {2013}%\smallskip\\
\end{rSection}
%WUStL Deans List                  			\hfill  {2011 - 2012}\smallskip\\
%\textit{Phi Eta Sigma} National Honors Society                     	\hfill  {2009}\smallskip\\
%Tulane Honors Program \hfill {2009}\smallskip\\
%Tulane Deans List                  			\hfill  {2008 - 2009}\smallskip\\
%Tulane Presidential Scholar (\$96,000) 				\hfill  {2008 - 2009}%\\
%{\scriptsize $\cdot$  {\em N.B.} : I declined this merit scholarship when I transferred institutions.}
%\vspace{-4mm}\begin{center}\footnotesize{ *upcoming* %or \textit{in progress}
%}\end{center} \vspace{-4mm}
%\end{rSection}
%----------------------------------------------------------------------------------------
%	Administration
%----------------------------------------------------------------------------------------
\begin{samepage}\begin{rSection}{\textrm{Administration}}Co-Director. Kelly/Connolly Longitudinal Study on Personality and Aging\hfill Dec 2012 - Present\smallskip\\
%Lab Manager. Rodgers Lab, Vanderbilt  \hfill Aug 2013 - Present\smallskip\\
Lab Coordinator. Strube Social Behavior Lab,  WUStL\hfill Oct 2012 - Jul 2013
\end{rSection}\end{samepage}%\newpage


%----------------------------------------------------------------------------------------
%	Publications
%----------------------------------------------------------------------------------------
\begin{rSection}{\textrm{Publications}}%:
\begin{etaremune}\item Jackson, J. J., Connolly, J. J., \meb, Leveille, M. M., \& Connolly, S. L. (forthcoming). Your friends know how long you will live: A 75-year study of peer-rated personality traits. \textit{Psychological Science}. \href{http://pss.sagepub.com/content/early/2015/01/12/0956797614561800.full}{\color{blue}{doi:10.1177/0956797614561800}}\\
{\scriptsize Select Press Coverage: 
%\href{http://news.yahoo.com/friends-could-predict-lifespan-study-133518737.html}{Agence France-Presse},%/Relax News/Yahoo},
%\href{http://www.ahchealthenews.com/2015/01/29/your-character-traits-may-predict-longevity/}{Advocate Health Care},
%\href{http://www.allvoices.com/article/100003352}{All Voices},
%\href{http://www.b.dk/viden/dine-venner-kan-spaa-om-hvornaar-du-doer}{Berlingske (Germany)},
%\href{http://www.business-standard.com/article/pti-stories/close-friends-know-how-long-you-ll-live-study-115012500160_1.html}{Business Standard},
%\href{http://www.bustle.com/articles/61765-your-friends-can-guess-when-youre-going-to-die-better-than-you-can-kind-of-creepy}{Bustle},
%\href{http://lifewise.canoe.ca/Living/YourLife/2015/01/26/22201566-relaxnews.html?cid=rsslifestyle}{Canoe (Quebec, Canada) },
%\href{http://www.cariereonline.ro/articol/vrei-sa-ai-succes-cariera-cu-cine-trebuie-sa-te-casatoresti}{Carriere Journal of Leadership (French)},
%\href{http://www.ctvnews.ca/lifestyle/your-friends-could-predict-your-lifespan-study-1.2207585}{CTV News},
%\href{http://www.dailymail.co.uk/health/article-2920097/Want-know-long-going-live-FRIENDS-accurate-judges-habits-send-early-grave.html}{Daily Mail},
%\href{http://www.dailyoffbeat.com/articles/6259/20150204/longevity-friends-friends-prediction-personality-traits.htm}{Daily Off Beat},
%\href{http://www.designntrend.com/articles/36443/20150125/long-will-live-ask-friends-study.htm}{Design Trend},
%\href{http://economictimes.indiatimes.com/magazines/panache/close-friends-know-how-long-youll-live-study/articleshow/46010003.cms}{Economic Times},
%\href{http://www.evoke.ie/extra/best-friends-study-predict-when-we-die/}{Evoke},
%\href{http://english.farsnews.com/newstext.aspx?nn=13931109000155}{FARS News Agency},
\href{http://www.fitnessandhealthyliving.com/do-friends-know-how-long-youll-live/}{Fitness \& Healthy Living},
%\href{http://www.healthcanal.com/mental-health-behavior/59338-friends’-personality-insights-may-predict-your-longevity.html}{Health Canal},
%\href{http://www.hindustantimes.com/sexandrelationships/friends-are-forever-they-can-even-predict-how-long-you-live/article1-1311034.aspx}{Hindustan Times},
%\href{http://www.hngn.com/articles/63545/20150125/life-span-could-be-predicted-most-accurately-by-your-best-friend.htm}{HNGN/Headline and Global News},
\href{http://www.huffingtonpost.com/wray-herbert/how-long-will-you-live-as_b_6184476.html}{Huffington Post},
%\href{http://lifestyle.iafrica.com/psychology/980235.html}{iAfrica.com},
%\href{http://infinityhousemagazine.com/2015/01/28/friends-indicate-life-length/}{Infinity House Magazine},
%\href{http://innerself.com/content/living/health/10100-do-your-buddies-know-how-long-you-ll-live.html}{InnerSelf},
%\href{http://post.jagran.com/close-friends-know-how-long-you-will-live-study-1422185008}{Jagran Post},
%\href{http://www.jhunewsletter.com/2015/02/05/personality-ratings-can-predict-life-expectancy-20891/}{Johns Hopkins Newsletter},
%\href{http://machineslikeus.com/news/your-friends-know-how-long-youll-live}{Machines Like Us},
%\href{http://www.thedailystar.net/quirky-science-63218}{Manila Daily Star},
%\href{http://www.medicaldaily.com/personality-traits-help-your-circle-friends-predict-your-life-span-313106}{Medical Daily},
%\href{http://medicalxpress.com/news/2015-01-friends-youll.html}{Medical Express},
%\href{http://www.mrctv.org/blog/your-best-friend-knows-when-you-will-die}{MRC TV},
%\href{http://health.ninemsn.com.au/article.aspx?id=8951264}{MSN-Australia},
%\href{http://www.msn.com/it-it/salute/featured/quando-moriremo-lo-sanno-i-nostri-amici/ar-AA8YGLY}{MSN-Italy},
%\href{http://www.msn.com/en-nz/lifestyle/other/your-friends-could-predict-your-lifespan-study/ar-AA8BpFx}{MSN-New Zealand},
%\href{http://www.mx.dk/viden/videnskab/story/12339687}{MX/MetroExpress(Germany)},
\href{http://nymag.com/scienceofus/2014/12/will-your-personality-kill-you-ask-your-pals.html}{New York Magazine}, % / Science of US},
%\href{http://news.dk/nyhed/1617527/dine-venner-ved-hvor-laenge-du-lever}{News DK},
%\href{http://www.newsmaxhealth.com/Health-News/longevity-prediction-death-friends/2015/01/26/id/620804/}{NewsMaxHealth},
%\href{http://www.psychologicalscience.org/index.php/news/releases/friends-personality-insights-predict-a-persons-longevity.html}{Psychological Science},
%\href{http://www.punchng.com/health/healthwise/friends-know-how-long-youll-live-study-finds-2/}{Punch},
%\href{http://psychcentral.com/news/2014/12/09/personality-as-defined-by-friends-may-predict-longevity/78392.html}{PyschCentral},
%\href{http://www.realsimple.com/health/preventative-health/relationship-good-for-health}{Real Simple},
%\href{http://www.youtube.com/watch?v=h0fLOHUUA0k}{Richard Fowler Show (YouTube)},
%\href{http://www.sciencecodex.com/friends_know_how_long_youll_live_study_finds-149493}{Science Codex},
%\href{http://www.sciencedaily.com/releases/2015/01/150124120813.htm}{Science Daily},
\href{http://www.smithsonianmag.com/science-nature/how-long-will-you-live-ask-your-friends-180954201/?no-ist}{Smithsonian Magazine},
%\href{http://www.sundayworld.com/style/health/can-friends-predict-your-life-expectancy}{Sunday World},
\href{http://www.theguardian.com/commentisfree/oliver-burkeman-column/2015/jan/27/your-friends-know-more-about-your-life-than-you-do-including-when-you-might-die}{The Guardian}
%,\href{http://thenewage.co.za/150105-12-53-Your_friends_could_predict_your_lifespan}{The New Age},
%\href{http://www.thesundaily.my/news/1309295}{The Sun Daily },
%\href{http://news.health.com/2015/01/29/the-weird-way-your-bridesmaids-can-predict-how-long-youll-live/}{Time/Time / News Health}%,
%\href{http://www.timeslive.co.za/lifestyle/2015/01/27/your-friends-could-predict-your-lifespan-study}{Times Live/New Zealand},
%\href{http://timesofindia.indiatimes.com/home/science/Close-friends-know-how-long-youll-live/articleshow/46016278.cms}{Times of India}
}
\end{etaremune}\end{rSection}\vspace{-4mm}

%----------------------------------------------------------------------------------------
%	Computer programs and documentation
%----------------------------------------------------------------------------------------
\begin{rSection}{\textrm{Software}}%:
\begin{etaremune}\item  Beasley, W., Rodgers, J. L., Bard, D., Hunter, M., \meb, \& Meredith, K. (2015). NlsyLinks: Utilities and kinship information for research with the NLSY \R package version 1.404 \href{http://liveoak.github.io/NlsyLinks}{\color{blue}{http://liveoak.github.io/NlsyLinks}}\end{etaremune}\end{rSection}\pagebreak

%----------------------------------------------------------------------------------------
%	Presentations
%----------------------------------------------------------------------------------------
\begin{rSection}{\textrm{Presentations}}\begin{etaremune}
\item \meb \& Rodgers, J. L. (June 2015). Additive effects of maternal conscientiousness and general ability on infant health. Poster to be presented at the 2015 Association for Research in Personality Conference, St. Louis, Missouri.%\pagebreak
\item\meb \& Rodgers, J. L. (April 2015). Kinship-based quasi-experimental designs. Talk to be given at the Quantitative Methods Colloquium, Department of Psychology \& Human Development, Vanderbilt University, Nashville, Tennessee.
\item \meb, Hadd, A. R., \& Rodgers, J. L. (February 2015). Impact of adolescent conscientiousness and intelligence on health at middle age: A sibling comparison approach. Poster presented at the 16th Annual Meeting of the Society for Personality and  Social Psychology, Long Beach, California. Also, presented at the 3rd Annual Lifespan Social-Personality Preconference, Long Beach, California.
\item Jackson, J. J., \textbf{Garrison, S. M.}, Connolly, J. J., \& Leveille, M. (February 2015). Using multiple perspectives to inform the association between personality and important life outcomes. Talk given at the 16th Annual Meeting of the Society for Personality and  Social Psychology, Long Beach, California.
\item\meb, Connolly, J. J., Leveille, M., \& Jackson, J. J. (February 2015). Agreeableness-Stress interactions explored: Within couple differences partially moderate the relationship between stress and divorce. Poster presented at the 3rd Annual Lifespan Social-Personality Preconference, Long Beach, California.
\item Romick, K.,\student \meb, \& Rodgers, J. L. (November 2014). Early book ownership: Catalyst for future reading enjoyment and achievement. Poster presented at the 2014 Tennessee Psychological Association Annual Convention, Nashville, Tennessee. \textit{Poster awarded 3\textsuperscript{rd} place in Undergraduate Poster Competition}
\item\meb, Hadd, A. R., \& Rodgers, J. L. (October 2014). The downstream health consequences of individual differences: Evidence from a kinship modeling perspective. Poster presented at the 2014 Tennessee Psychological Association Annual Convention, Nashville, Tennessee.
\item Connolly, J. J., Leveille, M., \meb, \& Jackson, J. J. (October 2014). Relief,  regret,  resilience: The  long-term  psychological  effects  of  getting divorced. Paper presented at the 28th Annual Convention of the Connecticut Psychological Association, Haddam, Connecticut.
\item\meb, Connolly, J. J., Leveille, M., \& Jackson, J. J. (July 2014). Your friends know when you will divorce: A dyadic Cox regression of peer-rated personality. Poster presented at the 17th Annual Meeting of the European Conference on Personality, Lausanne, Switzerland.
\item Jackson, J. J., \meb, Connolly, J. J., \& Leveille, M. (July 2014). Personality trait change in adulthood predicts health status in older adulthood. Talk given at the 17th Annual Meeting of the European Conference on Personality, Lausanne, Switzerland.
\item Rodgers, J. L., \meb, \& Hadd, A. R. (June 2014). Intelligence and Fertility in the NLSY79 Respondents: Children of Siblings and Biometrical Models. Paper presented at the 2014 Behavior Genetics Association, Charlottesville, Virginia. 
\pagestyle{myheadings}
\markright{\textrm{\em GARRISON}}
\item\meb, Hadd, A. R., \& Rodgers, J. L. (April 2014). Influence of adolescent intelligence and conscientiousness on health outcomes at middle age. Talk given at the Quantitative Methods Colloquium, Department of Psychology \& Human Development, Vanderbilt University, Nashville, Tennessee.
\item\begin{samepage}Hadd, A. R., \meb, \& Rodgers, J. L. (April 2014). The relationship between maternal IQ and home environment. Talk given at the Quantitative Methods Colloquium, Department of Psychology \& Human Development, Vanderbilt University, Nashville, Tennessee.\end{samepage}%\pagebreak
\item\begin{samepage}\meb, Connolly, J. J., Leveille, M., \& Jackson, J. J. (February 2014). Peer-rated personality traits influence relationship duration and dissolution. Poster presented at the 15th Annual Meeting of the Society for Personality and Social Psychology, Austin, Texas. Also, presented at the 2nd Annual Lifespan Social-Personality  Preconference, Austin, Texas.\end{samepage}
%\item\begin{samepage}\meb, Connolly, J. J., Leveille, M., \& Jackson, J. J. (February 2014). Peer-rated personality traits influence relationship duration and divorce. Poster presented at the 2nd Annual Lifespan Social-Personality  Preconference, Austin, Texas.\end{samepage}
\item\begin{samepage}Jackson, J. J., \textbf{Garrison, S. M.}, Connolly, J. J., \& Leveille, M. (February 2014). What your friends know that you don't: Friend rated personality predicts longevity 70 years later. Talk given at the 15th Annual Meeting of the Society for Personality and  Social Psychology, Austin, Texas.\end{samepage}
\item\begin{samepage}\meb (April 2013). Domestic dissatis{\em fiction}: Gender differences in a multilevel model of marital satisfaction. Poster presented at the Annual Psychology Honors Symposium, Washington  University, St. Louis, Missouri. Also, presented at the Annual Undergraduate Research Symposium, Washington University, St. Louis, Missouri.\end{samepage}
%\item\meb (April 2013). Domestic dissatisfaction: Gender differences in a multilevel model of marital satisfaction. Poster presented at the Annual Undergraduate Research Symposium, Washington University, St. Louis, Missouri.
\end{etaremune}\vspace{-3mm}\begin{center}\footnotesize{*denotes undergraduate student co-author*}\end{center} \vspace{-3mm}%\pagebreak
\end{rSection}
\pagestyle{myheadings}
\markright{\textrm{\em GARRISON}}
%----------------------------------------------------------------------------------------
%	Other Articles
%----------------------------------------------------------------------------------------
\begin{samepage}\begin{rSection}{\textrm{Popular Press Publications}} \begin{etaremune}
\item\textbf{Garrison, S. M.} (in press). How jealous are you? \textit{LoveLogica}.
\item\textbf{Garrison, S. M.} (in press). The Kinsey Scale. \textit{LoveLogica}.%\pagebreak
\item\textbf{Garrison, S. M.} (in press). How masculine AND feminine are you?: Gender roles and personality. \textit{LoveLogica}.
\item\textbf{Garrison, S. M.} (in press). %Are you ready for romance?: 
The romantic personality and relationship readiness. \textit{LoveLogica}.
\item\textbf{Garrison, S. M.} (in press). Attachment style and relationships. \textit{LoveLogica}.
\item\meb(in press). The science behind birds of a feather: Assortative mating on personality. \textit{LoveLogica}.
\end{etaremune}\end{rSection}\end{samepage}
%----------------------------------------------------------------------------------------
%	Abstracts
%----------------------------------------------------------------------------------------
\begin{samepage}\begin{rSection}{\textrm{Published Abstracts}}
\begin{etaremune}\item\meb (2013). Domestic dissatis{\em fiction} or dissatis{\em fact}ion?: Gender differences in a multilevel model of marital satisfaction using prenuptial marital expectations after 20 years. [Abstract] {\em Washington University Senior Honors Thesis Abstracts. 5}, 166.\end{etaremune}\end{rSection}\end{samepage}%\pagebreak

%----------------------------------------------------------------------------------------
%	Submitted/In prep Abstracts
%--------------------------------


%----------------------------------------------------------------------------------------
%	Current Projects
%----------------------------------------------------------------------------------------
\begin{rSection}{\textrm{Current Work}}
{\large {\bf Working Papers}}
\begin{etaremune}\item\meb, Connolly, J. J., Leveille, M., \& Jackson, J. J. (in prep). As time goes by: Personality predicts the timing of divorce over 45 years. Target: \textit{JPSP}
\item\meb, Hadd, A. R., \& Rodgers, J. L. (in prep). Adolescent conscientiousness and intelligence impact health at midlife: A genetically informed extension of the sibling comparison approach. Target: \textit{MBR}%\smallskip\\%\meb (commissioned). Are you too picky?: Extreme mate selectivity. \textit{LoveLogica}
\end{etaremune}
{\large {\bf Ongoing Analysis}}\begin{etaremune}
%\item Altruism and longevity (with Connolly \et)\smallskip\\
%Downstream consequences of divorce (with Connolly \et)\smallskip\\
%\item Downstream influences on reading: A genetically informed design. (with Romick)\smallskip\\
%\item Facial structure, attractiveness, and divorce (with Connolly \et)\smallskip\\
\item Flynn Effect and age at first intercourse (with Rodgers)
\item Genetically informed extension of the sibling comparison approach (with Rodgers \et)
% \item Generalizability of the Terman longitudinal study of the gifted\smallskip\\
%\item History of Lowell Kelly and his marriage study (with Connolly \et)\smallskip\\
%\item Life history narratives from the KCLS (with Connolly \et\smallskip\\
\item Personality's influence on partner health and longevity across multiple cohorts (with Jackson \et)
%\item Validity of the Kelly Personality Rating Scale (with Jackson \et)
\end{etaremune}{\large {\bf Software}}\begin{etaremune}
\item \meb. (2015). Mason: Quantitative Personality Functions \R package version $\alpha$ \color{blue}{\url{https://github.com/smasongarrison/Mason_R_Package}}
\end{etaremune}\end{rSection}

%\pagebreak
%----------------------------------------------------------------------------------------
%	Teaching
%----------------------------------------------------------------------------------------

\begin{rSection}{\textrm{Teaching
}}
{\large {\bf Laboratory Instructor}\\}
Introduction to Statistical Analysis. Prof. Joseph L. Rodgers, Vanderbilt\hfill  {Spring 2014}\\
\hspace* {6 mm}Lecture Topics: Excel Tutorials, Graphical Data Analysis, Hypothesis Testing,\\
\hspace* {6 mm}Probability Distributions, Scale Development, Statistical Literacy, Z-Scores%\pagebreak
\smallskip\\
Introduction to Statistical Analysis. Prof. James H. Steiger, Vanderbilt\hfill  {Fall 2013}\\
\hspace* {6 mm}Lecture Topics: Power and Effect Size, R Tutorials\medskip\\
{\large {\bf Teaching Assistant}}\\
Introduction to Statistical Analysis. Prof. Joseph L. Rodgers, Vanderbilt\hfill  {Spring 2014}\smallskip\\
Introduction to Statistical Analysis. Prof. James H. Steiger, Vanderbilt\hfill  {Fall 2013}\smallskip\\
Introduction to Social Psychology. Prof. Michael J. Strube, WUStL\hfill  {Fall 2012}\pagebreak\medskip\\
{\large {\bf Disability Support}}\\
Introduction to Statistical Analysis. Prof. Joseph L. Rodgers, Vanderbilt\hfill  {Spring 2015}\smallskip\\
Introduction to Statistical Analysis. Prof. Joseph L. Rodgers, Vanderbilt\hfill  {Spring 2014}
\end{rSection}%\pagebreak
%-------------------------------------------------------------------
%	Experience
%----------------------------------------------------------------------------------------

\begin{rSection}{\textrm{EXPERIENCE}}
{\large \textbf{Academic}}\\
User and Statistical Support, NLSY79 Kinship Links. Rodgers Lab, Vanderbilt\hfill Feb 2014; Aug 2014 - Present\smallskip\\%\pagebreak
Methods Consultant. Turiano Lab, West Virginia Univ. \hfill Mar 2014 - Present\smallskip\\
Graduate Researcher. Rodgers Lab, Vanderbilt\hfill Jul 2013 - Present\smallskip\\
Research Affiliate. Jackson Personality Measurement $\&$ Development Lab, WUStL \hfill Jul 2013 - Present\smallskip\\
Research Assistant. Jackson Personality Measurement $\&$ Development Lab, WUStL\hfill Aug 2012 - Jul 2013\smallskip\\
Research Assistant. Strube Social Behavior Lab, WUStL\hfill Jan 2012 - Oct 2012\medskip\\
{\large \textbf{Industry}}\\
Data Analysis Consultant. Feed the Arts\hfill Jun 2012 - Mar 2013; Jan 2015 - Present\smallskip\\
Assessment Consultant. SkilledUp\hfill Sep 2014\smallskip\\
Lead Test Developer. LoveLogica\hfill Feb 2014 - Dec 2014\smallskip\\
Assessment Consultant. Framew\"{u}rk\hfill Feb 2013; Apr 2014\smallskip\\
Assessment Consultant. ReviewNet\hfill May 2012 - Jun 2012\medskip\\%\pagebreak\\
{\large \textbf{Field Work}}\\
Visiting Researcher. Bentley Historical Library, Univ. of Michigan\hfill Jul 2014\smallskip\\
Visiting Researcher. Institute for Quantitative Social Science, Harvard \hfill Jan 2013%\smallskip\\
\end{rSection}%\pagebreak

%----------------------------------------------------------------------------------------
%	Service
%----------------------------------------------------------------------------------------
\begin{rSection}{\textrm{Service}}
{\large \textbf{National}}\\
Reviewer, APSSC Student Grant Competition\hfill{Dec 2014}\smallskip\\
Volunteer, Conference Transportation. SMEP Annual Meeting\hfill{Oct 2014}\smallskip\\
Reviewer, AERA Annual Meeting SIG-Cognition and Assessment\hfill{Aug 2014}\smallskip\\%\pagebreak
Reviewer, AERA Annual Meeting SIG-Test Validity Research and Evaluation\hfill{Aug 2014}\smallskip\\
Reviewer, APS Student Council Student Research Award\hfill{Mar 2014}\smallskip\\
Reviewer, SPSP Graduate Student Council Student Poster Award\hfill{Nov 2013}\medskip\\
{\large \textbf{Department \& University}}\\
Panelist, Doctoral Application Advice. Dept. of Psychology \& Human Dev., Vanderbilt\hfill {Apr 2014; \textit{Mar 2015}}\smallskip\\
Panelist, Graduate Application Advice. Psychological Sciences Honors Program, Vanderbilt\hfill {Sep 2014}\smallskip\\
Panelist, Graduate School Admissions. \textit{Psi Chi}, Vanderbilt\hfill {Sep 2013}\smallskip\\
President, Undergraduate Economics Association. Dept. of Economics, WUStL\hfill  {May 2011 - Dec 2011}\smallskip\\
Treasurer, Undergraduate Economics Association. Dept. of Economics, WUStL\hfill{May 2010 - May 2011}\smallskip\\
Marketing Executive, Undergraduate Economics Association. Dept. of Economics, WUStL\hfill  {Aug 2009 - May 2010}\medskip\\
{\large \textbf{Ad Hoc Journal Reviewer}}\\
Journal of Family Issues, %(Nov 2014; Jul 2014)
Journal of Research in Personality% (Feb 2015)
\\\vspace{-5mm}\begin{center}\footnotesize{ \textit{upcoming}% or 
%\textit{in progress}
}\end{center} \vspace{-2mm}
\end{rSection}

%----------------------------------------------------------------------------------------
%	Committees
%----------------------------------------------------------------------------------------
%\newpage 
\begin{rSection}{\textrm{Committees}}
{\large \textbf{Undergraduate Honors Theses Committees}}\\
Sloane Sparks (Apr 2014), \textit{Gender Differences in Emotional Intelligence: Positive Emotions and Appraisal Theory}.%\\
%\hspace* {6 mm}Currently, a graduate student at Vanderbilt School of Nursing.
\smallskip\\%\newpage
Lydia Fuller (Apr 2014), \textit{GED Student Achievement Trajectories and Predictors: Using the Latent Class Growth\\
\hspace* {6 mm}Model to Understand Heterogeneous Learning Patterns}.%\\
%\hspace* {6 mm}Currently, a consultant at Bain \& Company, with deferred admission to Yale Law School.
\end{rSection}\pagebreak

%----------------------------------------------------------------------------------------
%	Undergraduate Research Supervision
%----------------------------------------------------------------------------------------
%\newpage 
%\begin{rSection}{\textrm{Research Supervision}}
%{\large \textbf{Undergraduate}}\\
%Markiewitz, Nathan, Vanderbilt University\hfill{2013 - 2014}\smallskip\\
%Romick, Kayley, Vanderbilt University\hfill{2013 - Present}
%\end{rSection}%\newpage
%----------------------------------------------------------------------------------------
%	Outreach
%----------------------------------------------------------------------------------------
\begin{rSection}{\textrm{Outreach}}
Moderator. GradAdmissions, Reddit.com\hfill  {Jan 2015 - Present}\smallskip\\
%Contributor. Psychology Wikiproject, wikipedia.org\hfill {Dec 2014 - Present}\smallskip\\
Limited Moderator. AskScience, Reddit.com\hfill  {Sep 2014 - Present}\smallskip\\
Psychology Panelist, Expert AMA: Psychology \& Social Work Panel. AskSocialScience\hfill  {Apr 2014}\smallskip\\
Science Panelist, Quantitative Psychology. AskScience, Reddit.com\hfill  {Dec 2013 - Present}\smallskip\\%\newpage
Science Panelist, Individual Differences. AskSocialScience, Reddit.com\hfill  {Dec 2013 - Present}\smallskip\\
Member, Women in Science \& Engineering. School of Medicine, Vanderbilt\hfill  {Dec 2013 - Present}\smallskip\\%\newpage
Member, Peabody Queeries (Q.Ed). Peabody College, Vanderbilt\hfill  {Aug 2013 - Present}\smallskip\\
Member, Science Cafe. Adventure Science Center, Nashville, TN\hfill  {May 2013 - Present}\smallskip\\
Member, Pride Alliance. WUStL\hfill  {Aug 2009 - May 2013}
\end{rSection}
%\pagebreak


%---------------------
%----------------------------------------------------------------------------------------
%	Graduate Coursework
%----------------------------------------------------------------------------------------
\begin{rSection}{\textrm{Coursework}}
Item Response Theory \textrm{II}. Prof. S.-J. Cho, Vanderbilt\hfill  {\textit{Spring 2015}}\smallskip\\
Multilevel Modeling. Prof. K. Preacher, Vanderbilt\hfill  {\textit{Spring 2015}}\smallskip\\
Multivariate Statistics. Prof. J. Steiger, Vanderbilt\hfill  {\textit{Spring 2015}}\smallskip\\
Cognitive Science to the Classroom. Prof. B. Rittle-Johnson, Vanderbilt\hfill  {Fall 2014}\smallskip\\
Item Response Theory \textrm{I}. Prof. S.-J. Cho, Vanderbilt\hfill  {Fall 2014}\smallskip\\
Structural Equation Modeling. Prof. D. Cole, Vanderbilt\hfill  {Fall 2014}\smallskip\\%\newpage
Applied Bayesian Modeling. Profs. R. Bakker \& J. Karreth, Univ. of Michigan\hfill  {Summer 2014}\smallskip\\
Behavior Genetics. Prof. J. Rodgers, Vanderbilt\hfill  {Summer 2014}\smallskip\\
Data Mining. Prof. R. Stine, Univ. of Michigan\hfill  {Summer 2014}\smallskip\\
Exploratory \& Graphical Data Analysis. Prof. J. Rodgers, Vanderbilt\hfill  {Spring 2014}\smallskip\\
Psychological Measurement. Prof. D. Lubinski, Vanderbilt\hfill  {Spring 2014}\smallskip\\
Quantitative Methods \& Experimental Design. Prof. A. Tomarken, Vanderbilt\hfill  {Spring 2014}\smallskip\\
Correlation \& Regression. Prof. J. Rodgers, Vanderbilt\hfill  {Fall 2013}\smallskip\\
Gifted Learner: Characteristics \& Assessment. Prof. T. Stambaugh, Vanderbilt\hfill  {Fall 2013}\smallskip\\
First Year Research Seminar: Ethics \& Grant Writing. Profs. D. Levin \& R. Marois, Vanderbilt\hfill  {Fall 2013}\smallskip\\
Statistical Inference. Prof. J. Steiger, Vanderbilt\hfill  {Fall 2013}\smallskip\\
Quantitative Methods \textrm{II}. Prof. J. Jackson, WUStL\hfill  {Spring 2013}\smallskip\\
Quantitative Methods \textrm{I}. Prof. J. Jackson, WUStL\hfill  {Fall 2012}\smallskip\\
\begin{samepage}History and Modern Systems of Psychology. Prof. H. Roediger \textrm{III}, WUStL \hfill  {Spring 2012}\vspace{-2mm}\begin{center}\footnotesize{ %\textit{upcoming}% or 
\textit{in progress}
}\end{center} \vspace{-4mm}\end{samepage}
\end{rSection}
%\pagebreak
%----------------------------------------------------------------------------------------
%	Development
%----------------------------------------------------------------------------------------

%\begin{rSection}{\textrm{Development}}
%{\large \textbf{Methods $\&$ Substance}}\\
%General and Topical Data Archives. ICPSR Blalock Lecture Series, Univ. of Michigan\hfill  {Jun 2014}\smallskip\\
%Intro. to Human Behavioral Genetics. Coursera, Univ. of Minnesota\hfill  {May 2014 - Jun 2014}\smallskip\\
%Big Data and Social Physics. edX, MIT\hfill  {May 2014}\smallskip\\
%Statistical Analysis of fMRI Data. Coursera, Johns Hopkins\hfill  {Feb 2014 - Mar 2014}\smallskip\\
%Critical $\&$ Creative Thinking Models Across the Content Areas. Gifted Education Institute, Vanderbilt\hfill {Dec 2014}\smallskip\\
%Predoctoral Training in Experimental Education Research. Peabody College, Vanderbilt\hfill  {Jul 2013 - Present}\smallskip\\
%Social Epidemiology. Coursera, Univ. of Minnesota\hfill  {May 2013 - Jul 2013}%\newpage%
%\medskip\\
%{\large {\bf Teaching}}\\
%Teaching a Course for the First Time. Online Teaching Series, George Mason Univ.\hfill  {Jul 2014}\smallskip\\
%Flipped or Hybrid Courses. Online Teaching Series, George Mason Univ.\hfill  {May 2014}\smallskip\\
%How to Enter the Online Teaching Space. Online Teaching Series, George Mason Univ.\hfill  {Feb 2014}\smallskip\\
%Student Feelings and the Research Assignment. Writing Studio, Vanderbilt\hfill  {Nov 2013}\smallskip\\
%Using Chance Magazine to Engage Students in Statistics. Quant Methods Workshop, Vanderbilt\hfill  {Nov 2013}\smallskip\\
%Challenges Teaching Statistics \& Methods Courses. Quant Methods Workshop, Vanderbilt\hfill  {Sep 2013}\smallskip\\
%Incorporating Research and Design into STEM Classes. Center for Teaching, Vanderbilt\hfill  {Sep 2013}\smallskip\\
%Teaching Assistant Orientation. Center for Teaching, Vanderbilt\hfill  {Aug 2013}\smallskip\\
%Undergraduate Teaching Assistant and Peer Mentor Training. WUStL\hfill  {Aug 2012}
%\vspace{-2mm}\begin{center}\footnotesize{*upcoming* 
%or \textit{in progress}
%}\end{center} \vspace{-4mm}
%\end{rSection}
%\pagebreak
%----------------------------------------------------------------------------------------
%	Learned Skills
%----------------------------------------------------------------------------------------
%\pagebreak
\begin{rSection}{\textrm{Skills}}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} p{14cm} }

Certifications & Microsoft Office Access Specialist, Microsoft Office Excel Specialist\medskip\\
Coding & HTML, %Java (I only know enough to be dangerous), 
\LaTeX, Lua, Markdown, Python, \R \medskip\\
Languages & English, Latin\medskip\\
Select Software & %Adobe Illustrator, Amos,
BUGS/JAGS,
Eviews, %GIMP,
\href{https://github.com/smasongarrison}{Git}, % Google Analytics, 
LISREL, % Mechanical Turk, 
Mplus, %Mondrian, Oracle VirtualBox, PsychoPy, Qualtrics, 
\R, %REDCap, 
SAS, SPSS%/PSPP, SuperLab, Microsoft Office and other common productivity packages for Windows and OS platforms
\medskip\\
Statistics & Bayesian Methods, Biometrical Modeling%(\eg DF Analysis, MDAN Design)
, Classical Test Theory%(\eg Extrinsic Convergent Validation, Multitrait-Multimethod Matrices)
, Dyad Modeling, Exploratory Data Analysis, Factor Analysis, %fMRI Modeling,  
Generalized Linear Modeling%(\eg ANCOVA, Regression), 
, Item Response Theory, Monte Carlo Simulations, Multilevel Modeling, Robust Methods%(\eg Cross-Validation)
, Quasi-Experimental Designs, Structure Equation Modeling, Survival Analysis %(\eg Additive Hazard, Cox Regression)
\end{tabular}

\end{rSection}
\pagebreak
%----------------------------------------------------------------------------------------
%	Memberships
%----------------------------------------------------------------------------------------
\begin{samepage}\begin{rSection}{\textrm{Memberships}}
\begin{tabular}{ l l }
American Educational Research Association (AERA)& Association for Psychological Science (APS) \\
$\cdot$ {\small Div D: Measurement and Research Methodology} &  Association for Research in Personality (ARP)\\
%$\cdot$ {\small SIG 68: Motivation; SIG 91: Giftedness}& Psychometric Society\\
American Psychological Association (APA) & Society for Personality and Social Psychology (SPSP)\\
$\cdot$ {\small Div 5: Evaluation, Measurement, and Statistics}
\\
$\cdot$ {\small Div 8: Personality and Social Psychology} \\
\end{tabular}
\end{rSection}\end{samepage}

%----------------------------------------------------------------------------------------
%	References
%----------------------------------------------------------------------------------------
%\pagebreak
\begin{samepage}\begin{rSection}{\textrm{References}}
%Available Upon Request
\begin{tabular}{ l l }
\begin{tabular}{@{}l@{}}\textbf{Joseph L. Rodgers, Ph.D} \\
Lois Autrey Betts Professor \\
Quantitative Methods Area Head \\
Department of Psychology $\&$ Human Development \\
Vanderbilt University, Peabody College\end{tabular} & 
\begin{tabular}{@{}l@{}}\textbf{Joshua J. Jackson, Ph.D}\\
Assistant Professor\\
Department of Psychology\\
Washington University in St. Louis\\\\\end{tabular} \bigskip\\
\begin{tabular}{@{}l@{}}\textbf{Lewis R. Goldberg, Ph.D}\\
Professor \textit{Emeritus} \\
Department of Psychology \\
University of Oregon\end{tabular} & 
\begin{tabular}{@{}l@{}}
\textbf{Michael J. Strube, Ph.D} \\
Professor \\
Department of Psychology\\
Washington University in St. Louis\end{tabular}\end{tabular}




\end{rSection}\end{samepage}
% OTHER REFS
%\begin{tabular}{@{}l@{}}\textbf{James J. Connolly, J.D/Ph.D} \\Director of the Kelly/Connolly Longitudinal Study\\ Connolly Consulting\end{tabular}
%\begin{tabular}{@{}l@{}}\textbf{Jeremy Biesanz, Ph.D} \\Associate Professor\\Department of Psychology\\ The University of British Columbia\end{tabular}



\end{document}
