%----------------------------------------------------------------------------------------
%	Teaching
%----------------------------------------------------------------------------------------
%\pagebreak
\begin{rSection}{\textrm{Teaching}}
\vspace*{2pt}
%\vspace{-1mm}\begin{center}\footnotesize{Modality: *Blended* $\dagger$Online$\dagger$}\end{center}\vspace{-4mm}
%\begin{minipage}{\linewidth}
{\large  \bf Instructor}\\
Citation Needed: {\small Psychology, Misinformation, \& Wikipedia} (392). {\footnotesize WFU (taught occasionally; 1 total times)}\hfill{2026--Present}\\
Applied Data Science for Psychologists (279). {\footnotesize WFU (taught 1x/year; 1 total times)}\hfill{2026--Present}\\
Methods in Psychological Research (210/310). {\footnotesize WFU (taught 1--2x/year; 3 total times)}\hfill{2022--Present}\\
\hspace*{6 mm} \href{https://psychmethods.github.io/coursenotes/}{\color{blue} psychmethods.github.io/coursenotes/}\smallskip\\
Data Science for Psychologists in \R (703). {\footnotesize WFU (taught 1x/year; 4 total times)}\hfill{2021--Present}\\
\hspace*{6 mm} \href{https://datascience4psych.github.io/DataScience4Psych/}{\color{blue} datascience4psych.github.io/DataScience4Psych}\smallskip\\
Psychological Testing (362). {\footnotesize WFU (taught occasionally; 2 total times)}\hfill{2020--Present}\\
%\hspace*{6 mm} \href{https://www.youtube.com/playlist?list=PLKrrdtYgOUYYgag4erySD7L0jDcZGMlS_}{\color{blue} YouTube playlist}\quad
\hspace*{6 mm} \href{https://r-computing-lab.github.io/psychtesting/}{\color{blue} r-computing-lab.github.io/psychtesting}\smallskip\\
Personality (255). {\footnotesize WFU (taught 1--2x/year; 7 total times)}\hfill{2019--Present}\\
\hspace*{6 mm} \href{https://smasongarrison.github.io/personality/}{\color{blue} smasongarrison.github.io/personality} \smallskip\\
\begin{comment}
Methods in Psychological Research (210/310). Wake Forest University \hfill{Spring 2022; Fall 2024, \textit{Fall 2025}}\\
Data Science for Psychologists in \R (703). Wake Forest University\hfill{Spring 2023\textsuperscript{*}, Spring 2025}
\hspace*{6 mm} \href{https://datascience4psych.github.io/DataScience4Psych/}{\color{blue} datascience4psych.github.io/DataScience4Psych}\hfill{Spring 2021\textsuperscript{*}; Spring 2022}\smallskip\\
Psychological Testing  (362). Wake Forest University \hfill{Spring 2020;\textsuperscript{*} \href{https://www.youtube.com/playlist?list=PLKrrdtYgOUYYgag4erySD7L0jDcZGMlS_}{\color{blue}Spring 2021\noteBns}}
\hspace* {6 mm} \href{https://r-computing-lab.github.io/psychtesting/}{\color{blue} r-computing-lab.github.io/psychtesting}\smallskip\\
%\pagebreak\\
Personality (255). Wake Forest University \hfill{Fall 2021; \href{https://www.youtube.com/playlist?list=PLKrrdtYgOUYZpENpYddjG8n_q3bfbx8Kr}{Fall 2022x2\noteBns}}\\
\hspace*{6 mm} \href{https://smasongarrison.github.io/personality/}{\color{blue} smasongarrison.github.io/personality}\hfill{Fall 2019; Spring 2020;\textsuperscript{*} \href{https://www.youtube.com/playlist?list=PLKrrdtYgOUYZpENpYddjG8n_q3bfbx8Kr}{\color{blue}Fall 2020x2\textsuperscript{*}\noteBns}}\smallskip\\
\hspace* {6 mm}\smallskip\\
\end{comment}
Introduction to Statistical Analysis (2110). Vanderbilt University\hfill {Fall 2018}\\
Lying with Statistics. Vanderbilt Summer Academy \hfill{Summer 2017}\\
Introduction to Applied Statistics. Vanderbilt Summer Academy \hfill{Summer 2016}\smallskip\\
%\end{minipage}
%\begin{minipage}{\linewidth}
\hspace* {-0 mm}{\large {\bf Laboratory Instructor}}\\
Introduction to Statistical Analysis. Prof. Joseph L. Rodgers, Vanderbilt\hfill{Spring 2014}\\
%\smallskip%\\\hspace* {6 mm}Lecture Topics: Excel Tutorials, Graphical Data Analysis, Hypothesis Testing,\\
%\hspace* {6 mm}Probability Distributions, Scale Development, Statistical Literacy, Z-Scores
%\smallskip\\
Introduction to Statistical Analysis. Prof. James H. Steiger, Vanderbilt\hfill{Fall 2013}%\\
%\hspace* {6 mm}Lecture Topics: Power and Effect Size, \R Tutorials
%\end{minipage}
\medskip\\
\begin{minipage}{\linewidth}{\large {\bf Teaching Assistant}}\\
Introduction to Statistical Analysis. Prof. Joseph L. Rodgers, Vanderbilt\hfill  {Spring 2014}\\
Introduction to Statistical Analysis. Prof. James H. Steiger, Vanderbilt\hfill  {Fall 2013}\\
Introduction to Social Psychology. Prof. Michael J. Strube, WUStL\hfill{Fall 2012}\end{minipage}\medskip\\
\begin{minipage}{\linewidth}{\large {\bf Disability Support}}\\
Introduction to Statistical Analysis. Prof. Joseph L. Rodgers, Vanderbilt\hfill  {Spring 2018}\\
Introduction to Statistical Analysis. Prof. Joseph L. Rodgers, Vanderbilt\hfill  {Spring 2015}\\
Introduction to Statistical Analysis. Prof. Joseph L. Rodgers, Vanderbilt\hfill{Spring 2014}\end{minipage}%\medskip\\
%\begin{minipage}{\linewidth}{\large {\bf Select Guest Lectures}}\\
%Markdown and chatgpt. AI Essentials for Academics, Wake Forest \hfill{July 2024}\\
%Using Mplus to Estimate Heritability. Behavior Genetics Workshop, Vanderbilt \hfill{July 2017}\\
%Personality and the Lifespan. Social \& Personality Development, Vanderbilt\hfill {April 2017}\end{minipage}
\end{rSection}
