%----------------------------------------------------------------------------------------
%	Teaching
%----------------------------------------------------------------------------------------
\begin{rSection}{\textrm{Teaching}}
\vspace*{2pt}
%\begin{minipage}{\linewidth}
{\large {\bf Instructor}\\}
Data Science for Psychologists in \R (703). Wake Forest University \hfill {\textit{Spring 2021}}\smallskip\\
Psychological Testing  (362). Wake Forest University \hfill {Spring 2020;\textsuperscript{*} \textit{Spring 2021}}\smallskip\\%\hfill{ \textit{Spring 2021} \notb }\smallskip\\
Personality (255). Wake Forest University\hfill{Fall 2019; Spring 2020;\textsuperscript{*} \textit{Fall 2020x2\textsuperscript{*}\notbns}}\smallskip\\
Introduction to Statistical Analysis (2110). Vanderbilt University\hfill {Fall 2018}\smallskip\\
Lying with Statistics. Vanderbilt Summer Academy \hfill{Summer 2017}\smallskip\\
Introduction to Applied Statistics. Vanderbilt Summer Academy \hfill{Summer 2016}%\vspace{2pt}
%\end{minipage}
\vspace{-2mm}\begin{center}\footnotesize{Format: *Blended* $\dagger$Online$\dagger$}\end{center}%\vspace{-1mm}
%\smallskip
\begin{minipage}{\linewidth}
{\large {\bf Laboratory Instructor}}\\
Introduction to Statistical Analysis. Prof. Joseph L. Rodgers, Vanderbilt\hfill{Spring 2014}%\\
%\smallskip\\\hspace* {6 mm}Lecture Topics: Excel Tutorials, Graphical Data Analysis, Hypothesis Testing,\\
%\hspace* {6 mm}Probability Distributions, Scale Development, Statistical Literacy, Z-Scores
\smallskip\\
Introduction to Statistical Analysis. Prof. James H. Steiger, Vanderbilt\hfill{Fall 2013}%\\
%\hspace* {6 mm}Lecture Topics: Power and Effect Size, \R Tutorials
\end{minipage}
\medskip\\
\begin{minipage}{\linewidth}{\large {\bf Teaching Assistant}}\\
Introduction to Statistical Analysis. Prof. Joseph L. Rodgers, Vanderbilt\hfill  {Spring 2014}\smallskip\\
Introduction to Statistical Analysis. Prof. James H. Steiger, Vanderbilt\hfill  {Fall 2013}\smallskip\\
Introduction to Social Psychology. Prof. Michael J. Strube, WUStL\hfill{Fall 2012}\end{minipage}\medskip\\
\begin{minipage}{\linewidth}{\large {\bf Disability Support}}\\
Introduction to Statistical Analysis. Prof. Joseph L. Rodgers, Vanderbilt\hfill  {Spring 2018}\smallskip\\
Introduction to Statistical Analysis. Prof. Joseph L. Rodgers, Vanderbilt\hfill  {Spring 2015}\smallskip\\
Introduction to Statistical Analysis. Prof. Joseph L. Rodgers, Vanderbilt\hfill{Spring 2014}\end{minipage}\medskip\\
\begin{minipage}{\linewidth}{\large {\bf Guest Lectures}}\\
Using Mplus to Estimate Heritability. Behavior Genetics Workshop, Vanderbilt \hfill{July 2017}\\
Personality and the Lifespan. Social \& Personality Development, Vanderbilt\hfill {April 2017}\end{minipage}
\end{rSection}
