%----------------------------------------------------------------------------------------
%	Other Conference Presentations
%----------------------------------------------------------------------------------------
%\hspace*{-8mm}{\large {\bf Departmental Talks}}

\item\meb (Fall 2019). Using families to test causal claims without experiments. Talk to be given at Experimental Area , Department of Psychology, The University of North Carolina at Greensboro. 

%\item\meb (Invited Dec 2018). Using families to test causal claims without experiments. Talk to be given at Department of Psychology, Saint John's University, Bronx, NY. 
%\item\meb (Invited Nov 2018). Using families to test causal claims without experiments. Talk to be given at Department of Psychology, Montclair State University, Montclair, NJ. 
\item\meb \& \Joe (Nov 2018). Using families to test causal claims without experiments. Talk given at Quantitative Methods Colloquium, Department of Psychology \& Human Development, Vanderbilt University. 
\item\meb (Oct 2018). Using families to test causal claims without experiments. Talk given at Department of Psychology, Wake Forest University. 
\item\meb \& \Joe (Mar 2018). Using siblings to test causal claims without experiments. Talk given at Quantitative Methods Colloquium, Department of Psychology \& Human Development, Vanderbilt University. 
\item\meb \& \Joe (Apr 2017). Twins, Cousins, and Sibling-Pairs (oh my): Biometrical Applications of 42,773 Kinship Pairs. Talk given at Quantitative Methods Colloquium, Department of Psychology \& Human Development, Vanderbilt University. \href{https://osf.io/uyqwd/}{\color{blue}{https://osf.io/uyqwd/}}
\item\meb \& \Joe (Apr 2016). Multivariate Biometrical Study of the Link between SES and Health Outcomes. Talk given at Quantitative Methods Colloquium, Department of Psychology \& Human Development, Vanderbilt University.
\item \meb (Feb 2016) Who you marry matters: Partner traits influence your own mortality. Talk given at Health Psychology Area Workshop, Department of Psychology, University of British Columbia. \href{https://osf.io/jbf96/}{\color{blue}{https://osf.io/jbf96/}}
\item \meb (Nov 2015) Who you marry matters: Partner characteristics influence your own longevity and other important outcomes. Talk given at Junior Fellows Speaker Series, St. John's College, University of British Columbia. \href{https://osf.io/zqv5t/}{\color{blue}{https://osf.io/zqv5t/}}
\item\meb \& \Joe (Apr 2015). Smarter girls \textit{really don't} delay sex: An extended discordant siblings model. Talk given at Quantitative Methods Colloquium, Department of Psychology \& Human Development, Vanderbilt University.
\item\meb, Hadd, A. R., \& \Joe (Apr 2014). Influence of adolescent intelligence and conscientiousness on health outcomes at middle age. Talk given at Quantitative Methods Colloquium, Department of Psychology \& Human Development, Vanderbilt University. 

\hspace*{-8mm}{\large {\bf Departmental Presentations}}
\item Hadd, A. R., \meb, \& Rodgers, J. L. (Apr 2014). The relationship between maternal IQ and home environment. Talk given at Quantitative Methods Colloquium, Department of Psychology \& Human Development, Vanderbilt University.
\item\meb \& Strube, M. J. (Apr 2013). Domestic dissatis{\em fiction}: Gender differences in a multilevel model of marital satisfaction. Poster presented at Annual Psychology Honors Symposium, Washington University in St. Louis. Also, presented at Annual Undergraduate Research Symposium, WUStL.
\smallskip\\
