%----------------------------------------------------------------------------------------
%	Talks
%----------------------------------------------------------------------------------------
\item\meb (Jan 2020). Using families to test causal claims without experiments. Talk given at Experimental Area, Department of Psychology, The University of North Carolina at Greensboro. 
%\item\meb (Invited Dec 2018). Using families to test causal claims without experiments. Talk to be given at Department of Psychology, Saint John's University, Bronx, NY. 
%\item\meb (Invited Nov 2018). Using families to test causal claims without experiments. Talk to be given at Department of Psychology, Montclair State University, Montclair, NJ. 
\item\meb (Oct 2018). Using families to test causal claims without experiments. Talk given at Department of Psychology, Wake Forest University. 
\item \meb (Feb 2016) Who you marry matters: Partner traits influence your own mortality. Talk given at Health Psychology Area Workshop, Department of Psychology, University of British Columbia. \href{https://osf.io/jbf96/}{\small\color{blue}{osf.io/jbf96/}}
\item \meb (Nov 2015) Who you marry matters: Partner characteristics influence your own longevity and other important outcomes. Talk given at Junior Fellows Speaker Series, St. John's College, University of British Columbia. \href{https://osf.io/zqv5t/}{\small\color{blue}{osf.io/zqv5t/}}

\hspace*{-8mm}{\large {\bf Conference Talks}}

\item \meb \& \Joe (Jun 2019). Uncovering the Origins of Age at First Intercourse: Applications of an Extended-Family Behavior Genetic Model. Take given at 2019 Biennial Association for Research in Personality Conference in Grand Rapids, MI.
\item\meb, O'Keefe, P., Hunter, M., Beasley, W., Bard, D. \& \Joe (Jun 2018). AC'RE model: Estimating Rearing Effects without Twins Raised Apart. Talk given at Behavior Genetics Annual Meeting, Boston, MA.
\item\meb \& \joe (Sep 2016). Advances in discordant sibling designs from the NLSY, illustrated with SES and health. Talk given at Developmental Methods Annual Conference in Whitefish, MT.\smallskip\\
%
\hspace*{-8mm}{\large {\bf Conference Presentations}}

\item Hunter, M., \meb, Beasley W., O'Keefe, P.,  Bard, D., \&   \Joe, (Jun 2019). Five ways to analyze 50,000 pairs of related persons in the National Longitudinal Survey of Youth. Talk given at Behavior Genetics Annual Meeting, Stockholm, Sweden. 

\item Beasley W., Hunter, M., Bard, D., \meb, O'Keefe, P. \&  \Joe, (Jun 2019). Original and Replication Research with the NLSY79 and NLSY97 Kinship Links. Talk given at Behavior Genetics Annual Meeting, Stockholm, Sweden. 

\item Bard, D., Hunter, M., \meb, O'Keefe, P., Beasley W.,  \&  \Joe, (Jun 2019). Patterns of Phenotype-Environment Correlation within Cognitive Development. Talk given at Behavior Genetics Annual Meeting, Stockholm, Sweden. 

\item O'Keefe, P., \meb, Bard, D., Hunter, M.,  Beasley W.,  \&  \Joe, (Jun 2019). The Mediating Impact of Cognitive Ability on the SES-Health Gradient. Talk given at Behavior Genetics Annual Meeting, Stockholm, Sweden. 

\item \meb \& \Joe (Feb 2019). Uncovering the Origins of Age at First Intercourse: Applications of an Extended-Family Behavior Genetic Model. Poster presented at 2019 SPSP Annual Convention in Portland, OR. Also, presented at Personality Processes, Functions and Dynamics Preconference.


\item\Joe, \meb, O'Keefe, P., W., Bard, D., Hunter, M., \& Beasley (Jun 2018). Responding to a 100-Year-Old Challenge from Fisher: A Biometrical Analysis of Adult Height in the NLSY Data Using Only Cousin Pairs. Talk given at Behavior Genetics Annual Meeting, Boston, MA. 

\item\meb (Mar 2018). Do Commonly-Used Factor Analysis Criteria Work?: Monte-Carlo Simulations of Personality-Like Data. Poster presented at 2018 SPSP Annual Convention in Atlanta, GA. 
 %
\item\meb (Jun 2017). Effectiveness of factor enumeration rules on personality data. Poster presented at 2017 Association for Research in Personality in Sacramento, CA.
%
\item\meb \& \joe (Jan 2017). Making Causal Claims without Experiments: Advances in Discordant Sibling Designs with the SES-health Gradient. Poster presented at 2017 SPSP Annual Convention in San Antonio, TX. Also, presented at Annual Lifespan Social-Personality Preconference.
%
\item\meb \& \joe (Oct 2016). Decomposing the Causes of the SES-Health Gradient with Biometrical Modeling. Poster presented at Annual Society of Multivariate Experimental Psychology (SMEP) Graduate Student Conference in Richmond, VA.
%
\item \meb, Connolly, J. J., Leveille, M., \& Jackson, J. J. (Jan 2016). When does personality influence the timing of divorce?: A dyadic Aalen regression of peer-rated personality over 45 years. Poster presented at Annual Meeting of the Society for Personality and Social Psychology, San Diego, CA. Also, presented at Annual Lifespan Social-Personality Preconference.
%
\item Zhu, J. Y., \meb, Rodgers, J. L. \& Zald, D. H. (Jan 2016). Shaping Perseverance: Evidence of shared environmental effects on Grit and a task-based measure of persistence. Poster presented at Annual Meeting of the Society for Personality and Social Psychology, San Diego, CA.
\item Jackson, J. J., \meb, Connolly, J. J., \& Leveille, M. (Jan 2016). Longevity findings from the KCLS. Flash talk given at Annual Social Personality Health Preconference, San Diego, CA. % Get title from Josh
%
\item Rodgers, J. L. \& \meb (Sep 2015). Do intelligent girls delay age at first intercourse?: Different results within-families versus between-families. Talk given at International Society for Intelligence Research Annual Conference in Albuquerque, NM.
%
\item \meb \& Rodgers, J. L. (Jun 2015). Additive effects of maternal conscientiousness and general ability on infant health: Cause or Confound? Poster presented at 2015 Association for Research in Personality Conference, St. Louis, MO.%\pagebreak
\item \meb, Hadd, A. R., \& Rodgers, J. L. (Feb 2015). Impact of adolescent conscientiousness and intelligence on health at middle age: A sibling comparison approach. Poster presented at Annual Meeting of the Society for Personality and Social Psychology, Long Beach, CA. Also, presented at Annual Lifespan Social-Personality Preconference.
\item Jackson, J. J., \textbf{Garrison, S. M.}, Connolly, J. J., \& Leveille, M. (Feb 2015). Using multiple perspectives to inform the association between personality and important life outcomes. Talk given at Annual Meeting of the Society for Personality and Social Psychology, Long Beach, CA.
\item\meb, Connolly, J. J., Leveille, M., \& Jackson, J. J. (Feb 2015). Agreeableness-Stress interactions explored: Within couple differences partially moderate the relationship between stress and divorce. Poster presented at Annual Lifespan Social-Personality Preconference, Long Beach, CA.
%
\item Romick, K.,\student \meb, \& Rodgers, J. L. (Nov 2014). Early book ownership: Catalyst for future reading enjoyment and achievement. Poster presented at 2014 Tennessee Psychological Association Annual Convention, Nashville, TN. \textit{Poster awarded 3\textsuperscript{rd} place in Undergraduate Poster Competition}
\item\meb, Hadd, A. R., \& Rodgers, J. L. (Oct 2014). The downstream health consequences of individual differences: Evidence from a kinship modeling perspective. Poster presented at 2014 Tennessee Psychological Association Annual Convention, Nashville, TN.
\item Connolly, J. J., Leveille, M., \meb, \& Jackson, J. J. (Oct 2014). Relief, regret, resilience: The long-term psychological effects of getting divorced. Paper presented at Annual Convention of the Connecticut Psychological Association, Haddam, CT.
\item\meb, Connolly, J. J., Leveille, M., \& Jackson, J. J. (Jul 2014). Your friends know when you will divorce: A dyadic Cox regression of peer-rated personality. Poster presented at Annual Meeting of the European Conference on Personality, Lausanne, Switzerland.
\item Jackson, J. J., \meb, Connolly, J. J., \& Leveille, M. (Jul 2014). Personality trait change in adulthood predicts health status in older adulthood. Talk given at Annual Meeting of the European Conference on Personality, Lausanne, Switzerland.
\item Rodgers, J. L., \meb, \& Hadd, A. R. (Jun 2014). Intelligence and Fertility in the NLSY79 Respondents: Children of Siblings and Biometrical Models. Paper presented at 2014 Behavior Genetics Association, Charlottesville, VA. 

\item\meb, Connolly, J. J., Leveille, M., \& Jackson, J. J. (Feb 2014). Peer-rated personality traits influence relationship duration and dissolution. Poster presented at Annual Meeting of the Society for Personality and Social Psychology, Austin, TX. Also, presented at Annual Lifespan Social-Personality Preconference.
\item Jackson, J. J., \textbf{Garrison, S. M.}, Connolly, J. J., \& Leveille, M. (Feb 2014). What your friends know that you don't: Friend rated personality predicts longevity 70 years later. Talk given at Annual Meeting of the Society for Personality and Social Psychology, Austin, TX.

\vspace{-2mm}\begin{center}\footnotesize{*denotes undergraduate student co-author*}\end{center} \vspace{-3mm}

%----------------------------------------------------------------------------------------
%	Other Conference Presentations
%----------------------------------------------------------------------------------------

\hspace*{-8mm}{\large {\bf Departmental Talks \& Presentations}}
\item\meb (Feb 2020). I don’t go looking for Data … Data usually finds me. Talk given at Seminar in Analysis and Measurement, Department of Psychology, Wake Forest University. 

\item\meb \& \Joe (Nov 2018). Using families to test causal claims without experiments. Talk given at Quantitative Methods Colloquium, Department of Psychology \& Human Development, Vanderbilt University. 

\item\meb \& \Joe (Mar 2018). Using siblings to test causal claims without experiments. Talk given at Quantitative Methods Colloquium, Department of Psychology \& Human Development, Vanderbilt University. 
\item\meb \& \Joe (Apr 2017). Twins, Cousins, and Sibling-Pairs (oh my): Biometrical Applications of 42,773 Kinship Pairs. Talk given at Quantitative Methods Colloquium, Department of Psychology \& Human Development, Vanderbilt University. \href{https://osf.io/uyqwd/}{\small\color{blue}{https://osf.io/uyqwd/}}
\item\meb \& \Joe (Apr 2016). Multivariate Biometrical Study of the Link between SES and Health Outcomes. Talk given at Quantitative Methods Colloquium, Department of Psychology \& Human Development, Vanderbilt University.

\item\meb \& \Joe (Apr 2015). Smarter girls \textit{really don't} delay sex: An extended discordant siblings model. Talk given at Quantitative Methods Colloquium, Department of Psychology \& Human Development, Vanderbilt University.
\item\meb, Hadd, A. R., \& \Joe (Apr 2014). Influence of adolescent intelligence and conscientiousness on health outcomes at middle age. Talk given at Quantitative Methods Colloquium, Department of Psychology \& Human Development, Vanderbilt University. 

\item Hadd, A. R., \meb, \& Rodgers, J. L. (Apr 2014). The relationship between maternal IQ and home environment. Talk given at Quantitative Methods Colloquium, Department of Psychology \& Human Development, Vanderbilt University.
\item\meb \& Strube, M. J. (Apr 2013). Domestic dissatis{\em fiction}: Gender differences in a multilevel model of marital satisfaction. Poster presented at Annual Psychology Honors Symposium, Washington University in St. Louis. Also, presented at Annual Undergraduate Research Symposium, WUStL.
\smallskip\\

