%----------------------------------------------------------------------------------------
%	Working Papers in review
%----------------------------------------------------------------------------------------
\item \meb (in prep). Fitting Problems: notes on evaluating model fit

\item \meb, Hunter, M., \& Burt, A. (in prep). Visualizing Heritability.

\item Hunter, M., \meb, \& Burt, A. (in prep). A note on the analytic identification of variance component models common to behavior genetics.

\item \meb \& \joe. (in revision) Using genetically-informed designs to test causal claims without experiments: Discordant-Sibling designs and applications. \href{https://osf.io/zpdwt/}{\small\color{blue}{osf.io/zpdwt/}}%\textit{European Journal of Personality}

\item\meb, Connolly, J. J., Leveille, M., \& Jackson, J. J. (in prep). As time goes by: Personality predicts the timing of divorce over 45 years.%Target: \textit{JPSP}
\item \meb \& \joe.  (in prep). ACRE: Twins raised apart without twins.
\item \meb. (in prep). Custom Model Selection Criteria for Factor Enumeration with Personality data.
\item \meb. (in prep). Model Selection Criteria for ACE models.
\item Stephenson, E., \meb, Lam, M., Biesanz, J., \& DeLongis, A. (in prep). Mediation in Multivariate Dyadic Survival Analysis: Findings from the Alameda Study. %Target: \textit{NEJM} 
\item Schweinsberg, M., Feldman, M., Staub, N., ..., \meb ...., Uhlmann, E.L. (under review). Radical dispersion in empirical results when independent scientists operationalize and test the same hypothesis with the same data. %Target: Science
%\item Zhu, J. Y., \meb, Hunter, M., Rodgers, J. L., \& Zald, D. H. (under revision). Shaping perseverance: Evidence of shared environmental effects on grit and a task-based measure of persistence. %PID
%\vspace{-2mm}\begin{center}\footnotesize{*made an equal contribution*}\end{center} \vspace{-3mm}
\vspace{-2mm}\begin{center}\end{center} \vspace{-4mm}
