%----------------------------------------------------------------------------------------
%	Publications
%----------------------------------------------------------------------------------------
\begin{rSection}{\textrm{Publications}}%:
\begin{etaremune}
\item\Joe, \meb, O'Keefe, P., W., Bard, D., Hunter, M., \& Beasley (in press). Responding to a 100-Year-Old Challenge from Fisher: A Biometrical Analysis of Adult Height in the NLSY Data Using Only Cousin Pairs.  \textit{Behavior Genetics}.
\item \meb \& \joe (2019) Decomposing the Causes of the Socioeconomic Status-Health Gradient with Biometrical Modeling. \textit{Journal of Personality and Social Psychology} \href{https://osf.io/vd2kc/}{\small\color{blue}{osf.io/vd2kc/}}
\item The Psychological Science Accelerator Team (2018). The Psychological Science Accelerator: Advancing Psychology Through a Distributed Collaborative Network. \textit{Advances in Methods and Practices in Psychological Science}, \href{https://psyarxiv.com/785qu/}{\small\color{blue}{psyarxiv.com/\allowbreak 785qu/}}
\item \meb. (2018). Popular Structural Equation Modeling Programs for Behavior Genetics. \textit{Structural Equation Modeling: A Multidisciplinary Journal}, 25:6, 972-977 \href{https://www.tandfonline.com/doi/abs/10.1080/10705511.2018.1493385}{\small\color{blue}{doi:\allowbreak 10.1080/10705511.2018.1493385}}
\item\meb, Doane, M. J., \& Elliott, M. (2018). Gay and Lesbian Experiences of Discrimination, Health, and Well-Being Surrounding the Presidential Election. \textit{Social Psychological \& Personality Science}, 9(2), 131-142. \href{https://dx.doi.org/10.17605/OSF.IO/DWSCM}{\small\color{blue}{osf.io/dwscm/}}
\item Schultz, L., Connolly, J. J., \meb, Leveille, M., Jackson, J. J. (2017). Vocational Interests Across 20 Years of Adulthood: Stability, Change, and the Role of Work Experiences. \textit{Journal of Research in Personality}, 71, 46-56.
\item\meb \& \Joe (2016). Casting doubt on the causal link between intelligence and age at first intercourse: A cross-generational sibling comparison design using the NLSY. \textit{Intelligence, 59}, 139-156. \href{http://www.sciencedirect.com/science/article/pii/S0160289616300162}{\small\color{blue}{doi:10.1016/\allowbreak j.intell.2016.08.008}}
\item Rodgers, J. L., Beasley, W. H., Bard, D. E., Meredith, K. M., Hunter, M., Johnson, A. B., Buster, M., Li, C., May, K. O., \meb, Miller, W. M., van den Oord, E., \& Rowe, D. C. (2016). The NLSY kinship links: Using the NLSY79 and NLSY-Children data to conduct genetically-informed and family-oriented research. \textit{Behavior Genetics}. \href{http://dx.doi.org/10.1007/s10519-016-9785-3}{\small\color{blue}{doi:\allowbreak 10.1007/s10519-016-9785-3}}
%
\item Jackson, J. J., Connolly, J. J., \meb, Leveille, M. M., \& Connolly, S. L. (2015). Your friends know how long you will live: A 75-year study of peer-rated personality traits. \textit{Psychological Science, 26}(3), 335-340.\\ \href{http://pss.sagepub.com/content/26/3/335}{\small\color{blue}{doi:\allowbreak 10.1177/0956797614561800}}
%\vspace{-2mm}\begin{center}\footnotesize{*made an equal contribution*}\end{center} \vspace{-3mm}
\end{etaremune}\end{rSection}%\vspace{-4mm}