%----------------------------------------------------------------------------------------
%	Talks
%----------------------------------------------------------------------------------------

\item\meb, O'Keefe, P., Hunter, M., Beasley, W., Bard, D. \& \Joe (Jun 2018). AC'RE model: Estimating Rearing Effects without Twins Raised Apart. Talk given at 48th Behavior Genetics Annual Meeting, Boston, MA. 
%\item\meb \& \Joe (Fall 2017). Using Siblings to Untangle the Causal Link between SES and Health Outcomes. %Talk to be given at Social and Personality Psychology Brown Bag, Department of Psychology, Texas A \& M, College Station, TX.
\item\meb \& \joe (Sep 2016). Advances in discordant sibling designs from the NLSY, illustrated with SES and health. Talk given at Developmental Methods $3^{rd}$ Annual Conference in Whitefish, MT.\smallskip\\
%
\hspace*{-8mm}{\large {\bf Conference Presentations}}
\item \meb \& \Joe (Feb 2019). Uncovering the Origins of Age at First Intercourse: Applications of an Extended-Family Behavior Genetic Model. Poster to be presented at 2019 SPSP Annual Convention in Portland, OR. Also, to be presented at Personality Processes, Functions and Dynamics Preconference.

\item\Joe, \meb, O'Keefe, P., W., Bard, D., Hunter, M., \& Beasley (Jun 2018). Responding to a 100-Year-Old Challenge from Fisher: A Biometrical Analysis of Adult Height in the NLSY Data Using Only Cousin Pairs. Talk given at 48th Behavior Genetics Annual Meeting, Boston, MA. 

\item\meb (Mar 2018). Do Commonly-Used Factor Analysis Criteria Work?: Monte-Carlo Simulations of Personality-Like Data.  Poster presented at 2018 SPSP Annual Convention in Atlanta, GA. 
 %
\item\meb (Jun 2017). Effectiveness of factor enumeration rules on personality data.  Poster presented at 2017 Association for Research in Personality in Sacramento, CA.
%
\item\meb \& \joe (Jan 2017). Making Causal Claims without Experiments: Advances in Discordant Sibling Designs with the SES-health Gradient. Poster presented at 2017 SPSP Annual Convention in San Antonio, TX. Also, presented at 5$^{th}$ Annual Lifespan Social-Personality  Preconference.
%
\item\meb \& \joe (Oct 2016). Decomposing the Causes of the SES-Health Gradient with Biometrical Modeling. Poster presented at $14^{th}$ Annual Society of Multivariate Experimental Psychology (SMEP) Graduate Student Conference in Richmond, VA.
%
\item \meb, Connolly, J. J., Leveille, M., \& Jackson, J. J. (Jan 2016). When does personality influence the timing of divorce?: A dyadic Aalen regression of peer-rated personality over 45 years. Poster presented at 17$^{th}$ Annual Meeting of the Society for Personality and Social Psychology, San Diego, CA. Also, presented at 4$^{th}$ Annual Lifespan Social-Personality  Preconference.
%
\item Zhu, J. Y., \meb, Rodgers, J. L. \& Zald, D. H. (Jan 2016). Shaping Perseverance: Evidence of shared environmental effects on Grit and a task-based measure of persistence. Poster presented at 17$^{th}$ Annual Meeting of the Society for Personality and Social Psychology, San Diego, CA.
\item Jackson, J. J., \meb, Connolly, J. J., \& Leveille, M. (Jan 2016). Longevity findings from the KCLS. Flash talk given at Annual Social Personality Health Preconference, San Diego, CA. % Get title from Josh
%
\item Rodgers, J. L. \& \meb (Sep 2015). Do intelligent girls delay age at first intercourse?:  Different results within-families versus between-families. Talk given at International Society for Intelligence Research Annual Conference in Albuquerque, NM.
%
\item \meb \& Rodgers, J. L. (Jun 2015). Additive effects of maternal conscientiousness and general ability on infant health: Cause or Confound? Poster presented at 2015 Association for Research in Personality Conference, St. Louis, MO.%\pagebreak
\item \meb, Hadd, A. R., \& Rodgers, J. L. (Feb 2015). Impact of adolescent conscientiousness and intelligence on health at middle age: A sibling comparison approach. Poster presented at 16th Annual Meeting of the Society for Personality and  Social Psychology, Long Beach, CA. Also, presented at 3$^{rd}$ Annual Lifespan Social-Personality Preconference.
\item Jackson, J. J., \textbf{Garrison, S. M.}, Connolly, J. J., \& Leveille, M. (Feb 2015). Using multiple perspectives to inform the association between personality and important life outcomes. Talk given at 16$^{th}$ Annual Meeting of the Society for Personality and  Social Psychology, Long Beach, CA.
\item\meb, Connolly, J. J., Leveille, M., \& Jackson, J. J. (Feb 2015). Agreeableness-Stress interactions explored: Within couple differences partially moderate the relationship between stress and divorce. Poster presented at 3$^{rd}$ Annual Lifespan Social-Personality Preconference, Long Beach, CA.
%
\item Romick, K.,\student \meb, \& Rodgers, J. L. (Nov 2014). Early book ownership: Catalyst for future reading enjoyment and achievement. Poster presented at 2014 Tennessee Psychological Association Annual Convention, Nashville, TN. \textit{Poster awarded 3\textsuperscript{rd} place in Undergraduate Poster Competition}
\item\meb, Hadd, A. R., \& Rodgers, J. L. (Oct 2014). The downstream health consequences of individual differences: Evidence from a kinship modeling perspective. Poster presented at 2014 Tennessee Psychological Association Annual Convention, Nashville, TN.
\item Connolly, J. J., Leveille, M., \meb, \& Jackson, J. J. (Oct 2014). Relief,  regret,  resilience: The  long-term  psychological  effects  of  getting divorced. Paper presented at 28$^{th}$ Annual Convention of the Connecticut Psychological Association, Haddam, CT.
\item\meb, Connolly, J. J., Leveille, M., \& Jackson, J. J. (Jul 2014). Your friends know when you will divorce: A dyadic Cox regression of peer-rated personality. Poster presented at 17$^{th}$ Annual Meeting of the European Conference on Personality, Lausanne, Switzerland.
\item Jackson, J. J., \meb, Connolly, J. J., \& Leveille, M. (Jul 2014). Personality trait change in adulthood predicts health status in older adulthood. Talk given at 17$^{th}$ Annual Meeting of the European Conference on Personality, Lausanne, Switzerland.
\item Rodgers, J. L., \meb, \& Hadd, A. R. (Jun 2014). Intelligence and Fertility in the NLSY79 Respondents: Children of Siblings and Biometrical Models. Paper presented at 2014 Behavior Genetics Association, Charlottesville, VA. 

\item\meb, Connolly, J. J., Leveille, M., \& Jackson, J. J. (Feb 2014). Peer-rated personality traits influence relationship duration and dissolution. Poster presented at 15$^{th}$ Annual Meeting of the Society for Personality and Social Psychology, Austin, TX. Also, presented at 2$^{nd}$ Annual Lifespan Social-Personality  Preconference.
\item Jackson, J. J., \textbf{Garrison, S. M.}, Connolly, J. J., \& Leveille, M. (Feb 2014). What your friends know that you don't: Friend rated personality predicts longevity 70 years later. Talk given at 15$^{th}$ Annual Meeting of the Society for Personality and  Social Psychology, Austin, TX.

\vspace{-2mm}\begin{center}\footnotesize{*denotes undergraduate student co-author*}\end{center} \vspace{-3mm}


