%----------------------------------------------------------------------------------------
%	Talks
%----------------------------------------------------------------------------------------

\item\meb, O'Keefe, P., Hunter, M., Beasley, W., Bard, D. \& \Joe (Jun 2018). AC'RE model: Estimating Rearing Effects without Twins Raised Apart. Talk to be given at 48th Behavior Genetics Annual Meeting, Boston, MA. 
%\item\meb \& \Joe (Fall 2017). Using Siblings to Untangle the Causal Link between SES and Health Outcomes. %Talk to be given at Social and Personality Psychology Brown Bag, Department of Psychology, Texas A \& M, College Station, TX.
\item\meb \& \Joe (Mar 2018). Using siblings to test causal claims without experiments.. Talk given at Quantitative Methods Colloquium, Department of Psychology \& Human Development, Vanderbilt University, Nashville, TN. 
\item\meb \& \Joe (Apr 2017). Twins, Cousins, and Sibling-Pairs (oh my): Biometrical Applications of 42,773 Kinship Pairs. Talk given at Quantitative Methods Colloquium, Department of Psychology \& Human Development, Vanderbilt University, Nashville, TN. \href{https://osf.io/uyqwd/}{\color{blue}{https://osf.io/uyqwd/}}
\item\meb \& \joe (Sep 2016). Advances in discordant sibling designs from the NLSY, illustrated with SES and health. Talk given at Developmental Methods $3^{rd}$ Annual Conference in Whitefish, MT.
\item\meb \& \Joe (Apr 2016). Multivariate Biometrical Study of the Link between SES and Health Outcomes. Talk given at Quantitative Methods Colloquium, Department of Psychology \& Human Development, Vanderbilt University, Nashville, TN.
\item \meb (Feb 2016) Who you marry matters: Partner traits influence your own mortality. Talk given at Health Psychology Area Workshop, Department of Psychology, University of British Columbia, Vancouver, BC. \href{https://osf.io/jbf96/}{\color{blue}{https://osf.io/jbf96/}}
\item \meb (Nov 2015) Who you marry matters: Partner characteristics influence your own longevity and other important outcomes. Talk given at Junior Fellows Speaker Series, St. John's College, University of British Columbia, Vancouver, BC. \href{https://osf.io/zqv5t/}{\color{blue}{https://osf.io/zqv5t/}}
\item\meb \& \Joe (Apr 2015). Smarter girls \textit{really don't} delay sex: An extended discordant siblings model. Talk given at Quantitative Methods Colloquium, Department of Psychology \& Human Development, Vanderbilt University, Nashville, TN.
\item\meb, Hadd, A. R., \& \Joe (Apr 2014). Influence of adolescent intelligence and conscientiousness on health outcomes at middle age. Talk given at Quantitative Methods Colloquium, Department of Psychology \& Human Development, Vanderbilt University, Nashville, TN.
