{\large \textbf{Administration}}\\
Moderator. \bluelinkreg{http://www.reddit.com/r/AcademicPsychology}{AcademicPsychology, Reddit.com}\hfill{Mar 2019 - Present}\smallskip\\
Limited Moderator. \bluelinkreg{http://www.reddit.com/r/Science}{Science, Reddit.com}\hfill{May 2015 - Present}\smallskip\\
Moderator. \bluelinkreg{http://www.reddit.com/r/GradAdmissions}{GradAdmissions, Reddit.com}\hfill{Jan 2015 - Present}\smallskip\\
Limited Moderator. \bluelinkreg{http://www.reddit.com/r/AskScience}{AskScience, Reddit.com}\hfill{Sep 2014 - Present}\medskip\\
%\pagebreak
%
%
{\large \textbf{Select Ongoing Engagement}}\smallskip\\
%
Member, \bluelinkreg{https://darndisability.org/}{Disability Advocacy and Research Network} \hfill{Jun 2022 - Present}\smallskip\\
Member, \bluelinkreg{https://disabledacademicco.wixsite.com/mysite}{Disabled Academic Collective} \hfill{Jan 2022 - Present}\smallskip\\
Member, \bluelinkreg{https://heterodoxacademy.org/}{Heterodox Academy} \hfill{Aug 2020 - Present}\smallskip\\
Data Doctor, \bluelinkreg{https://www.wikitree.com}{WikiTree} \hfill{Apr 2018 - Present}\smallskip\\
Member, Union of Concerned Scientists \hfill{Jan 2017 - Present}\smallskip\\
Science Verified User. \bluelinkreg{http://www.reddit.com/r/science}{Science, Reddit.com}\hfill{May 2015 - Present}\smallskip\\
Science Panelist, Quantitative Psychology. \bluelinkreg{http://www.reddit.com/r/AskScience}{AskScience, Reddit.com}\hfill{Dec 2013 - Present}\smallskip\\%\newpage
Science Panelist, Individual Differences. \bluelinkreg{http://www.reddit.com/r/AskSocialScience}{AskSocialScience, Reddit.com}\hfill{Dec 2013 - Present}\smallskip\\
Member, Statistics without Borders\hfill{Dec 2016 - Oct 2020}\smallskip\\
Member, Women in Science \& Engineering. School of Medicine, Vanderbilt\hfill{Dec 2013 - Jun 2019}\smallskip\\
Member, Peabody Queeries (Q.Ed). Peabody College, Vanderbilt\hfill{Aug 2013 - Jun 2019}\medskip\\
{\large \textbf{Panelist \& Participation}}\\
Panelist, Quantitative Psychology Information Session. QUAD Squad.\hfill{Oct 2020; Oct 2021;}\newline 
\hspace*{\hfill{Sept 2022; Nov 2023}\smallskip\\}
Panelist, Science AMA: Graduate School. \bluelinkreg{http://www.reddit.com/r/AskScience}{AskScience, Reddit.com}\hfill{Oct 2015}\smallskip\\
Volunteer, Genome BC. Community Science Celebration, Science World\hfill{Sep 2015}\smallskip\\
Panelist, Expert AMA: Psychology \& Social Work. \bluelinkreg{http://www.reddit.com/r/AskSocialScience}{AskSocialScience, Reddit.com}\hfill{Apr 2014}%\smallskip\\
