%----------------------------------------------------------------------------------------
%	Service
%----------------------------------------------------------------------------------------
{\large \textbf{Global \& National}}\\
Elected EMCR Member. IDEA Committee, Behavior Genetics Association \hfill{Jun 2023 – Present}\\ % Early- and mid-career researcher; Inclusion, Diversity, Equity, and Access; elected position
Member, IDEA Task Force, Behavior Genetics Association \hfill{Jun 2021 – Present}\\
Founding Member, Quantitative Access and Diversity (QUAD) Squad. \hfill{Sept 2020 – Present}\\%
\bluelinkreg{https://stats.foldingathome.org/donor/SMasonGarrison}{Volunteer}. \bluelinkreg{https://foldingathome.org/about/}{Folding\allowbreak $@$home}: Distributed computing project for simulating protein dynamics \hfill{Mar 2020 – Present}\\
Co-Organizer. Quantitative Psychology Info Session. QUAD Squad. \hfill{Sept 2022; Nov 2023;}\newline
\hspace*{0pt}\hfill{Oct 2020; Oct 2021}\smallskip\\
Judge for Thompson and Rowe awards. BGA Annual meeting\hfill{Jun 2022; Jun 2023}\\
Diversity Lunch Host. BGA Meeting\hfill{Jun 2023, Jun 2024}\\%on topics related to ''How can we make behavior genetics research more diverse?'' 
Mentor Lunch Host on ''Diversity in Behavior Genetics.'' BGA Meeting\hfill{Jun 2023, Jun 2024}\\
Member, Methodology and Data Analysis Committee. Psychological Science Accelerator\hfill{Sep 2017 – Jun 2021}\\
Mentor Lunch. ARP Biannual Meeting\hfill{Jun 2019}\\
Peer-Advisor. SPSP Annual Meeting\hfill{Feb 2019}\\
Student Conference Organizer. SMEP 2017 Meeting \hfill{Jun 2017 – Jun 2018}\\
Email Support, On-Site. Div 5, Teaching Statistics Conference\hfill{Mar 2017}\\
Volunteer, On-Site. SPSP Annual Meeting \hfill{Jan 2016}\\
Volunteer, Conference Transportation. SMEP 2014  \hfill{Oct 2014}\medskip\\
{\large \textbf{University \& Department}}\\
Member, Policies and Procedures. Dept. of Psychology, WFU\hfill{Jul 2024 – Present;}\newline 
\hspace*{0pt}{\hfill{Aug 2022 – July 2023}}\smallskip\\
Member, Faculty Advising Board, Center for Learning, Access, and Student Success, WFU\hfill {Feb 2022 – Present}\\
Major Advisor, Dept. of Psychology, WFU\hfill{Jan 2022 – Present}\\
Library Coordinator, Dept. of Psychology, WFU\hfill {Sep 2021 – Present}\\
Organizer, Seminar in Analysis and Measurement (SAM), Dept. of Psychology, WFU\hfill{Jul 2024 – Present;}\newline 
\hspace*{0pt}{\hfill{Sep 2021 – Jul 2023}}\smallskip\\
Co-Organizer, Seminar in Analysis and Measurement (SAM), Dept. of Psychology, WFU\hfill {Jul 2020 – Aug 2021}\\
Member, Job Search Committee for Human Neuroscience, Dept. of Psychology, WFU\hfill {Jul 2024- Present}\\
Panelist, Careers in Psychology Panel. Summer Immersion Program Psychology Institute, WFU\hfill {Jun 2024x2; Jun 2025x2}\\ % 2x in Jun
Member, Archie Award Selection Committee, Wake Forest College, WFU\hfill{Apr 2023}\\ 
Member, Social Media Committee. Dept. of Psychology, WFU\hfill {Sep 2019 – Jul 2022}\\
Member, Job Search Instructions Working Group. Dept. of Psychology, WFU\hfill{May 2020}\\
Co-Leader, Moving Forward: Listening Session on Climate and DEI, Dept. of Psychology, WFU\hfill {Nov 2019}\\
Panelist, Path to Graduate School Panel. Dept. of Psychology, UBC\hfill {Sep 2015}\\
Panelist, Doctoral Application Advice. Dept. of Psychology \& Human Dev., Vanderbilt\hfill {Apr 2014; Mar 2015}\\
Panelist, Graduate Application Advice. Psychological Sciences Honors Program, Vanderbilt\hfill {Sep 2014}\\
Panelist, Graduate School Admissions. \textit{Psi Chi}, Vanderbilt\hfill{Sep 2013}\\
President, Undergraduate Economics Association. Dept. of Economics, WUStL\hfill{May 2011 – Dec 2011}\\
\begin{minipage}{\linewidth}\vspace{1.1mm} Treasurer, Undergraduate Economics Association. Dept. of Economics, WUStL\hfill{May 2010 – May 2011}\\
Marketing Executive, Undergraduate Economics Association. Dept. of Economics, WUStL\hfill {Aug 2009 – May 2010}\end{minipage}\medskip\\
%
%
\begin{minipage}{\linewidth}\vspace{1.1mm} {\large \textbf{Editorial Boards}}\\
Graduate Advisor (General Statistics), Undergraduate Journal of Psychology, UBC\hfill{Sep 2015 – May 2018}\\
Graduate Advisor (Health Psychology), Undergraduate Journal of Psychology, UBC\hfill{Sep 2015 – May 2018}\end{minipage}\medskip\\
%\newpage
{\large \textbf{Ad Hoc Reviewer}}\\
\begin{tabular}{ @{} >{}l @{\hspace{6ex}} p{14cm} }

Books & Guilford Press\\
\medskip
Journals & Behavior Genetics \bigcdot %(Aug 2020),  feb
 % & \textit{Behavior Research Methods} \\%\bigcdot % (nov 2021) withdrew because omicron
 Canadian Journal of Behavioural Sciences \bigcdot %(May 2016, Aug)
 European Journal of Personality  \bigcdot %(Mar 2018)
 \textit{Frontiers in Genetics}  \bigcdot %(jan)
 Group Processes \& Intergroup Relations \bigcdot %(Apr 2020)
 Intelligence \bigcdot %(Sept 2016, multiple)
 Journal of Family Issues \bigcdot %(Nov 2014; Jul 2014)
 Journal of Family Psychology \bigcdot %(Jun 2019)
 Journal of Open Psychology Data \bigcdot %(aug 2021)
 Journal of Open Source Software \bigcdot %(april 2023;2025)
 Journal of Personality Assessment \bigcdot % (Oct 2020)
 The \R Journal \bigcdot % (Jul 2021)
 Journal of Research in Personality \bigcdot % (Feb 2015)
 %\textit{Rehabilitation Psychology}\bigcdot % (sept 2024)
 Structural Equation Modeling: A Multidisciplinary Journal \bigcdot % (Jul 2020)(Jun 2021)
 Psicologia: Reflex\~ao e Crítica \bigcdot %(Jun 2020)
 \textit{Psychological Methods} \bigcdot % (nov 2021) oct 2022, May 23
 Psychometrika \bigcdot % (Mar 2020)
 Translational Issues in Psychological Science\\% Sept 2015, nov 2019
\medskip %
Awards & APA Div 44 Trans Research Award \bigcdot %july 2016
APSSC Student Research Award \bigcdot %Mar 2014}
BGA Thompson Award \bigcdot %jun 2022
BGA Rowe Award \bigcdot %jun 2022
BGA Rising Star Award \bigcdot %jun 2022
SPSP Graduate Student Poster Award \bigcdot%Nov 2013}
SPSP Graduate Student Travel Award %jul 2021
\end{tabular}
\\ %
\begin{tabular}{ @{} >{}l @{\hspace{6ex}} p{14cm} }
Conferences & AERA Annual Meeting SIG-Cognition and Assessment \bigcdot %\hfill{Aug 2014} 
AERA Annual Meeting SIG-Test Validity Research and Evaluation \bigcdot %Aug 2014}
APS Annual Meeting Quantitative Area \bigcdot %2025}
SPSP Annual Meeting Undergraduate Posters \bigcdot %Sept2015}
SPSP Annual Meeting Single Presentation \bigcdot %Aug2021
SPSP Reviewing Inside the Grant Panel \bigcdot %jan22
SPSP Annual Meeting Symposia\\ %Aug2021}
\\ %
Grants & APS SC Student Grant Competition \bigcdot %Dec 2014
National Science Foundation Graduate Research Fellowship Program\\% \bigcdot %Dec 2020 ; jan 22
\end{tabular}

