%{\large \textbf{Diversity}}\\
%
%\smallskip\\
{\large \textbf{Research}}\\
An Introduction to Social Network Analysis in Psychology. Online Webinar, American Psychological Association \hfill{Apr 2016}\smallskip\\
Data Mining. Prof. R. Stine, U. of Michigan\hfill{Summer 2014}\smallskip\\
Intro. to Human Behavioral Genetics. Coursera, U. of Minnesota\hfill{Summer 2014}%May 2014 - Jun 2014}
\smallskip\\
General and Topical Data Archives. ICPSR Blalock Lecture Series, U. of Michigan\hfill{Jun 2014}\smallskip\\
Big Data and Social Physics. edX, MIT\hfill{Summer 2014}%May 2014}
\smallskip\\
Critical \& Creative Thinking Models Across the Content Areas. Gifted Education Institute, Vanderbilt\hfill{Dec 2014}\smallskip\\
Statistical Analysis of fMRI Data. Coursera, Johns Hopkins\hfill{Winter 2014}%Feb 2014 - Mar 2014}
\smallskip\\
Social Epidemiology. Coursera, U. of Minnesota\hfill{Summer 2013}%May 2013 - Jul 2013}
\smallskip\\
Predoctoral Training in Experimental Education Research. Peabody College, Vanderbilt\hfill{Jul 2013 - Present}\smallskip\\
%
%
{\large {\bf Teaching}}\\
 LGBTQI Inclusivity & Allyship in Learning Spaces.  Center for Teaching, Vanderbilt\hfill{\textit{Feb 2017}}\smallskip\\
Health Professional Teaching Skills. edX, U. of Toronto \hfill{Fall 2016}%Sept 2016}
Concept Mapping Your Course: Introduction and First Steps. Vanderbilt Summer Academy \hfill{Apr 2016}\smallskip\\
Mixing It Up: Instructional \& Classroom Management. Vanderbilt Summer Academy \hfill{Mar 2016}\smallskip\\
Crafting Effective Teaching Statements. Center for Teaching, Vanderbilt\hfill{Feb 2016}\smallskip\\
Using PowerPoint in teaching QM. Quant Methods Workshop, Vanderbilt\hfill{Feb 2016}\smallskip\\
Teaching a Course for the First Time. Online Teaching Series, George Mason U.\hfill{Jul 2014}\smallskip\\
Flipped or Hybrid Courses. Online Teaching Series, George Mason U.\hfill{May 2014}\smallskip\\
How to Enter the Online Teaching Space. Online Teaching Series, George Mason U.\hfill{Feb 2014}\smallskip\\
Student Feelings and the Research Assignment. Writing Studio, Vanderbilt\hfill{Nov 2013}\smallskip\\
Using Chance Magazine to Engage Students in Statistics. Quant Methods Workshop, Vanderbilt\hfill{Nov 2013}\smallskip\\
Challenges Teaching Statistics \& Methods Courses. Quant Methods Workshop, Vanderbilt\hfill{Sep 2013}\smallskip\\
Incorporating Research and Design into STEM Classes. Center for Teaching, Vanderbilt\hfill{Sep 2013}\smallskip\\
Teaching Assistant Orientation. Center for Teaching, Vanderbilt\hfill{Aug 2013}\smallskip\\
Undergraduate Teaching Assistant and Peer Mentor Training. WUStL\hfill{Aug 2012}