%----------------------------------------------------------------------------------------
%	Working Papers in review
%----------------------------------------------------------------------------------------
%\newpage
% Revision Under review

%{\large \textbf{Manuscripts conditionally accepted}}
{\large \textbf{Manuscripts Conditionally Accepted}}
\begin{etaremune}
\item Tierney, W., Cyrus-Lai, W., Hoogeveen, S., Haaf, J. M., Landy, J. F., Hardy, J. H., Ebersole, C. R., van den Bergh, D., Clemente, E. G., Pfeiffer, T., Dreber, A., Johannesson, M., Clark, C. J., Mitchell, G., Tenney, E. R., Chin, J. M., Dang, H., \textbf{Emotion Expression Forecasting Collaboration}, \& Uhlmann, E. L. (conditionally accepted pending analytic review). Who respects an angry woman? A crowdsourced systematic reexamination of the relationships between gender, emotion expression, and status conferral. \textit{Psychological Science}.
\end{etaremune}
{\large \textbf{Manuscripts under review or revision}}
\begin{etaremune}



\item \meb  (submitted). ggpedigree: Visualizing Pedigrees with 'ggplot2' and 'plotly' \textit{Journal of Open Source Software}. \href{https://joss.theoj.org/papers/e5116b83b03e2740960d1153c45f9480}{\small\color{blue}{submission}}

\item Aczel, B. ... \meb..., Nosek, B. (Revision under review) Investigating the analytical robustness of the social and behavioural sciences. \textit{Nature}

\item Navarre, K. M. \noteB, Uliaszek, A., Masland, S. \& \meb. (Revision under review) Stigma by Design? The Role of Psychology Curriculum in Perpetuating and Preventing Borderline Personality Disorder Stigma \textit{Teaching of Psychology}

\item \meb, \jt, Lyu, X$\dagger$, Robertson, H.\noteA, McKinzie, L.\noteA, Thompson, S. H. E.\noteA, \& \joe. (revision under review). Sibling Models Can Test Causal Claims without Experiments: Applications for Psychology. \href{https://osf.io/zpdwt/}{\small\color{blue}{osf.io/zpdwt/}} \textit{AMPPS} %Not: European Journal of Personality

\item Burt, S. A., \meb, Lyu, X,$\dagger$ \joe, Carroll, S. L., Smith, Ken R., \& Hunter, M. D. (Revise and Resubmit) Inherited mtDNA contributes to longevity: Evidence from extended pedigrees with 176 million kinship pairs. \textit{eBioMedicine}%\textit{Nature Aging} %\textit{PNAS}

\item \meb, Tyson, H. K.*, \& Lyu, X,$\dagger$ (Invited Revision under Review). Pragmatic AI Integration in R Teaching: From Frustration to Facilitation.  In I. Katzarska-Miller, M. Jackson, \& M. Fortner,  (Eds.) \textit{Integrating Artificial Intelligence into the Psychology Classroom} Retrieved from the Society for the Teaching of Psychology: \href{http://teachpsych.org/ebooks/}{\small\color{blue}{teachpsych.org/ebooks/}}

\item Hunter, M. D., \meb, Lyu, X.,$\dagger$ Good, R.,$*\dagger$ Carroll, S. L., \& Burt, S. A. (Revise and Resubmit) Tracing the Right Path: Determination of Large Pedigree Segmentation and Relatedness. \textit{Behavior Genetics}


\item \meb \& \joe (Revise and Resubmit). Fitting Problems: Evaluating Model Fit in Behavior Genetic Models. \textit{Behavior Genetics}  \href{https://doi.org/10.31234/osf.io/qys83}{\small\color{blue}{10.31234/osf.io/qys83}}
%\pagebreak\\
\end{etaremune}
{\large \textbf{Invited manuscripts in progress}}
\begin{etaremune}
\item O'Connor, S. \& \meb (Accepted Proposal) Exploring factors differentiating individuals’ willingness to participate in behavior genetic research. Public Science Special Issue. \textit{Behavior Genetics}

\item \meb \& Fleeson, W. (Accepted Proposal). Artificial Intelligence and the Development of Personality Theory: Past, Present, and Future. Special Issue in \textit{Expanding Horizons in Personality Science}


\item \meb, and Good, R.\noteA (working paper) Foundations for genetically-informed research: A primer on sibling comparisons and family-based modeling. \textit{Pathways to Research in Psychology}. EBSCO.
\end{etaremune}
%\break
%\hspace{-0mm}{\large \textbf{Special Issue Submission}}
%


% Rejected, needs to find a new home

% Ready to Submit
%\item Hunter, M., \meb, Beasley W., O'Keefe, P.,  Bard, D., \& \Joe (full manuscript). Five ways to analyze 50,000 pairs of related persons in the National Longitudinal Survey of Youth.  Target: \textit{Psych Methods}
{\large \textbf{Select manuscripts in progress}}

\begin{etaremune}
\item \jt \& \meb (full manuscript). Introduction to Discord: An R package to manage, model, and simulation kinship-based designs. Target: \textit{JOSS}

%\item DeMeo, N., McCabe, K. O., ... \meb ... (full manuscript) Diversity and Inclusion in Big Five Conceptualization and Measurement.  Target: \textit{EJP}

\item Thompson, S. H. E. \noteA \& \meb (full manuscript). Reestablishing Income and Depression as Links to Age of First Intercourse Using a Sibling Comparison Model. Target: \textit{Behavior Genetics}

\item Rubin, J., Meese, W., \meb, et al. (in progress) Taking Account of Disability in Social and Personality Psychology: A State-of-the-Field Review.

\item Eftedal, N. H., \meb, Hunter, M. D., Eilertsen, E. M., Czajkowski, N. O., \& Burt, S. A. (in progress) Mitochondrial DNA explains more than one percent of the variation in school outcomes in Norway. 

%\item Good, R.,\noteA \yrh, \&  \meb (Proposal Submitted). Patterns of Alcohol Use in a Military Subsample: A Sibling Comparison Design. Proposal Submitted to \textit{Behavior Genetics} IDEA special issue.
%\item Webster, E.*, Jennings, J. M. \& \meb (Proposal Submitted). A Sibling Comparison of Drug Use, Education, and Cognitive Impairment. Proposal Submitted to \textit{Behavior Genetics} IDEA special issue.



%
% In Prep 80%+ manuscript
%\item \meb, Connolly, J. J., Leveille, M., \& \jjj (in prep). As time goes by: Personality predicts the timing of divorce over 45 years. Target: \textit{JPSP}
%

%\item MeGee, E. O., \meb, Naphan-Kingery, D. et al. (in prep) Equity Ethic. Target: TBD
%In Prep less than 80% manuscript





%\item \kl, \jt, \& \meb (in prep). Intergenerational consequences of divorce

%%%% Older
%\item \meb \& \joe.  (in prep). ACRE: Twins raised apart without twins.
%\item \meb. (in prep). Custom Model Selection Criteria for Factor Enumeration with Personality data.


%% Dead
%\item Stephenson, E., \meb, Lam, M., Biesanz, J., \& DeLongis, A. (in prep). Mediation in Multivariate Dyadic Survival Analysis: Findings from the Alameda Study. %Target: \textit{NEJM} 
%\item Zhu, J. Y., \meb, Hunter, M., Rodgers, J. L., \& Zald, D. H. (under revision). Shaping perseverance: Evidence of shared environmental effects on grit and a task-based measure of persistence. %PID

%\vspace{-2mm}\begin{center}\footnotesize{*made an equal contribution*}\end{center} \vspace{-3mm}
%\vspace{-2mm}\begin{center}\end{center} \vspace{-4mm}
\end{etaremune}