%----------------------------------------------------------------------------------------
%	Working talks/abstracts in review
%----------------------------------------------------------------------------------------

\item Milhollen, M.* Lyu, X$\dagger$ \&  \meb (Jun 2022). The Chinese Family Panel Study: An Opportunity to Combat WEIRDNESS in Behavior Genetics. Abstract submitted to be presented at Behavior Genetics Annual Meeting.

\item Webster, E.*  \& \meb (Jun 2022). Just Say No? – Untangling the Relationship between Education And Drug Use. Abstract submitted to be presented at Behavior Genetics Annual Meeting.

\item \meb (Jun 2022). Diversifying the Behavior Genetic Pipeline: Pathways and Strategies for Incorporating Undergraduate Students. Abstract submitted to be presented at Behavior Genetics Annual Meeting.

\item Robertson, H.,\noteA \jdt, \Joe \&  \meb (Jun 2022). Discordant-Sibling Designs on the Effects of Conscientiousness and Mental Health. Abstract submitted to be presented at Behavior Genetics Annual Meeting.

\item Good, R.,\noteA \yrh, \&  \meb (Jun 2022). Patterns of Alcohol Use in a Military Subsample: A Sibling Comparison Design. Abstract submitted to be presented at Behavior Genetics Annual Meeting.

\item Lyu, X$\dagger$ \&  \meb (Jun 2022). Leveraging the China Family Panel Study: An Estimation of Height Using Preliminary Kinship Links. Abstract submitted to be presented at Behavior Genetics Annual Meeting.

\item McKinzie, L,* Lyu, X$\dagger$ \& \meb (Jun 2022) Leveraging the power of sibling data to untangle the relationship between ADHD, SES, and academic achievement. Abstract submitted to be presented at Behavior Genetics Annual Meeting.
%

\item Thompson, S.* \& \meb (Jun 2022) Exploring Age of First Intercourse and its Relationship with Depression and Socioeconomic Status: A Sibling Comparison Model.  Abstract submitted to be presented at Behavior Genetics Annual Meeting.
%

%

%

%

%
